### 2021-02-20 exercise_0/writeup/MachineLearning1_group35.tex
Add files via upload

\documentclass[a4paper,12pt]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amssymb,amsfonts,stmaryrd, wasysym}
\usepackage{color}
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%% PRL-programm %%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
%%%%%%%%%%%%%%%%%%%%%%%% Kopf- & Fußzeile %%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[footsepline]{scrlayer-scrpage}
\pagestyle{scrheadings}
\clearscrheadfoot

\ihead{Machine Learning - Exercise 0}
\ifoot{\newline Christian Hatschka, Daniel Fangl, Esra Ceylan}
\ofoot{\newline \pagemark}

\begin{document}
\section{Group members}
	Daniel Fangl (01526097) has a bachelor in Software Engineering and is currently in the master course Software Engineering and Internet Computing. Christian Hatschka (01525634) and Esra Ceylan (01526801) have a bachelor in Mathematics and are currently in the master course Logic and Computation.

\section{Choice of datasets}
	We looked for datasets with different characteristics. As a classification data\-set we chose one that is comparatively small in size but high in dimension. Moreover it has some missing values. In contrast, our regression dataset has a large size but small dimension and does not contain any missing values. Because of the diversity in size, dimension and expressibility we picked these two datasets.

	To put it in a nutshell, the choice of the datasets relates to the different sources of inexactness. While the small dataset could have errors in form of missing values or a small sample size, the large dataset is limited by its small number of dimensions.

\section{Classification dataset}
	For the classification dataset we chose 'Internet Advertisements Data Set' from UCI ML Repository (http://archive.ics.uci.edu/ml/datasets/Internet+ Advertisements). This dataset contains various information about the geometry of images, links as well as phrases occuring in advertisements on internet pages.

	The goal of the classification is to determine whether an element of a webpage is an advertisement.

	This dataset has a rather small sample size of $3279$ instances, whereas $2821$ are non-ads and $458$ are ads.	
	The small portion of advertisements seemed like a possible source of error in the dataset at first. After consideration, the reason for this is probably that the number of non-advertisement elements on an internet page is much bigger than the number of advertisement elements. Perhaps they were trying to reduce the number of false positives and were cautious with declaring ads.

	Additionally, in our chosen dataset roughly $28$\% of the instances contain at least one missing attribute.

	Figure~\ref{fig:adsheight} shows a boxplot diagram of the distribution of heights of advertisements and non-advertisements. 
		\begin{figure}[h]
			\centering
			\includegraphics[width=0.7\linewidth]{images/ads_height}
			\caption{Boxplot of heights of (non-)advertisements}
			\label{fig:adsheight}
		\end{figure}

	Since this is a dataset from 1998, the data contained is relatively old and therefore might differ from todays advertisements.

\section{Regression dataset}
	For the regression we selected the dataset 'Diamonds' from Open ML \newline (https://www.openml.org/d/42225). It contains general information about the diamond as well as e.g. it's price, weight or measurements.

	The goal of the regression model is to predict the price of a diamond based on the given attributes.

	The dataset has in total $53940$ samples, $10$ attributes and no missing values. The attributes can be divided into the following types: \\

	\begin{tabular}[h]{l|l}
		Ordinal & Cut (quality of the cut) \\
			& Color (worst to best) \\
			& Clarity (worst to best) \\
		\hline
		Interval & Table width (width from top relative to widest point)\\
			& Depth (a ratio of x, y, z) \\
		\hline
		Ratio & Carat (weight) \\
			& x, y, z (length, width, depth in mm) \\
			& Price (in US Dollars) 
	\end{tabular} \\

	The following figures show the distribution of the values of different attributes of the diamond dataset.
	%Below there are some graphs to show the distribution of values among the data types.

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.7\linewidth]{images/diamond_cut}
		\caption{Quality of the cut}
		\label{fig:diamondcut}
	\end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.65\linewidth]{images/diamond_axis}
		\caption{Boxplot of the length, width, depth of diamonds}
		\label{fig:diamondaxis}
	\end{figure}
\end{document}

### 2021-02-20 exercise_1/paper/main.tex
Add files via upload

\documentclass[a4paper,11pt]{article}
\usepackage[a4paper,left=3.1cm,right=3.1cm,top=3cm,bottom=2.9cm]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amssymb,amsfonts,stmaryrd, wasysym}
\usepackage{color}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{multirow} %multirow in table

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{titling}
\usepackage{caption}
\captionsetup{font=footnotesize}

%%%%%%%%%%%%%%%%% Kopf- & Fußzeile %%%%%%%%%%%%%%%%%
\usepackage[footsepline]{scrlayer-scrpage}
\pagestyle{scrheadings}
\clearscrheadfoot
\title{Machine Learning - Exercise 1}
\author{Christian Hatschka, Daniel Fangl, Esra Ceylan}
\date{November 2020}
\ihead{\thetitle}
\ifoot{\newline \theauthor}
\ofoot{\newline \pagemark}
\setlength{\headheight}{15pt}
\setlength{\footheight}{29pt}

\begin{document}
\maketitle
\section{Group members}
    Daniel Fangl (01526097) has a bachelor in Software Engineering and is currently in the master course Software Engineering and Internet Computing. Christian Hatschka (01525634) and Esra Ceylan (01526801) both have a bachelor in Mathematics and are currently enrolled in the master course Logic and Computation.

\section{Classifier} 
    We chose the $k$-NN, decision tree and random forest algorithm for building classifiers. These algorithms have several different properties, advantages and disadvantages, because of which we chose them. In the following they are described a bit more in detail.

    \subsection*{$k$-NN}
        This algorithm can learn complex decision boundaries. The build classifier is easy to understand and interpret. Moreover, no training time is needed. However, scaling may be required to avoid wrong influence of attributes and changes in the training set can influence the decision boundaries greatly.

        In this algorithm we considered to vary the following parameters: number of considered neighbors, distance function, weight function for the samples and the algorithm used to compute the nearest neighbors.

%    \subsection*{(Multilayer) perceptron}
%        Perceptron is a very simple model for binary decisions. But as we do not only have binary problems multilayer perceptron is more suited for our datasets. Unfortunately, we did not cover this algorithm as detailed as the others in the lecture, we will not do an exhaustive evaluation for this particular classifier.

    \subsection*{Decision tree}
        The advantage of this algorithm is that no scaling is needed. Additionally, there are fewer problems with categorical data as the distance is not measured to build the classifer, e.g. like in $k$-NN. But a disadvantage is that a fully grown tree can be overfitted to the given data.

        We have many possibilities to change parameters, e.g. the maximum depth of the tree, the criterion to measure the quality of a split or the strategy used to choose the split at each node.

    \subsection*{Random forest} \label{subsec:random-forest}
        This algorithm exploits the advantages of decision trees but reduces its drawbacks. The classifier is rather robust and mostly still simple. As we are growing multiple decision trees this algorithm is rather slow compared to the previous ones.

        The random forest algorithm has many parameters which can be varied. As a random forest combines many decision trees, we have the possibility to change parameters of the decision tree algorithm and additionally, e.g. the number of trees, the weights associated with classes or whether bootstrap samples (.i.e. using only a subset of the features for each tree) are used when building trees or not.

\section{Evaluation} 
    For the evaluation of the obtained classifiers we will first, split our dataset in a test and a training set with the holdout method resp. 5-fold cross-validation before making any changes to the data, e.g. imputation or scaling. We do not manipulate the data in advance to prevent bias. In the holdout method we divided the data into a $\sim 75\%$ training and $\sim 25\%$ test set split.

    We decided to consider the following performance measures in this exercise, but we are not calculating all numbers for all datasets as not every performance measure is relevant for every dataset.

    \subsection{Accuracy}
        The accuracy describes which percentage of the test set was correctly classified. %In terms of the confusion matrix it is the sum of the diagonal divided by the sum of all elements of the matrix.
        This is a good measure when the classes are equally represented. It is however not so good when the classes are imbalanced, e.g. when diagnosing a rare sickness, the classifier could get a high accuracy by simply diagnosing all patients as healthy.

    \subsection{Recall}
        Recall is the number of true positives divided by the sum of the true positives and false negatives. %In terms of a $2\times2$ confusion matrix it would be the top left value divided by the sum of the first column. 
        This measure expresses how many of the real positive values the classifier actually classifies as positive.

    \subsection{Precision}
        Precision is the number of true positives divided by the number of all as positive classified values. %In terms of a $2\times2$ confusion matrix it would be the top left value divided by the sum of the first row.
        This measure expresses how many of the as true classified instances are actually true.

%    \subsection{Specificity}
%        Specificity is the same as Recall except it looks at the number of true negatives divided by the sum of the false positives and true negatives.

\section{Breast Cancer Diagnostic}
    For this problem a dataset was provided containing $30$ numeric attributes about the patients breasts. These attributes all vary in the range of values they can take. Figure~\ref{fig:breast-cancer_value_ranges} shows a boxplot diagramm of the value ranges of the attributes in our dataset with 285 samples, i.e. the difference between the largest and the smallest occurring value of each attribute in the dataset. It can be seen that the median is less than 1 as the ranges of many attributes are contained in the interval $[0,1]$. But there are also some attributes with different value ranges, e.g. the attribute 'area worst' has values in $[240;3\,216]$. 
    \begin{figure}[h!]
        \centering
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=0.9\textwidth]{exercise_1/paper/figures/breast_cancer_range_plot.png}
            \caption{Boxplot of the values ranges of the attributes}
            \label{fig:breast-cancer_value_ranges}
        \end{subfigure}
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=1\textwidth]{figures/breast_cancer_malignant_pie.png}
            \caption{Class distribution}
            \label{fig:breast-cancer_classes_pie}
        \end{subfigure}
        \caption{Figures for the Breast Cancer dataset}
        \label{fig:breast-cancer}
    \end{figure}

    The goal of the classification problem is to predict for $284$ patients whether they have a malignant event (true) or not (false) based on the given attributes of the patient. In our dataset the proportion of samples with resp. without a malignant event is about $1:2$ (see Figure~\ref{fig:breast-cancer_classes_pie}).

Because of the imbalanced classes and the importance for a patient with breast cancer to be positively classified, we chose recall and accuracy as the performance measures for this dataset.

    \subsection{$k$-NN}
        Since the given dataset has very different value ranges, the first issue we encountered was that we had to scale the attributes because the spread of values was vastly different. In order to eliminate a wrong influence of attributes we normalised them via min-max scaling resp. standard scaling using the built in tools in scikit-learn.

        Afterwards, we built different classifiers using different parameters, e.g. varying $k$ or changing the weight function. We evaluated these classifiers via $5$-fold cross-validation over the given training set. Our tests showed that using scaling yields to a better classifier, but it does not make a difference if the min-max scaler or the standard scaler is used. This was the reason why we did not include the scaling method explicitly in this documentation. Table~\ref{tbl:kNN_breast-cancer_cross-validation} shows some results for the accuracy and recall for different parameter settings of $k$ and the weight function. For each classifier the average performance of accuracy and recall and the respective standard deviation is stated.

        \begin{table}[h]
        \centering
            \begin{tabular}[h]{r|c|c|c|c|c|}
                \multirow{2}{*}{$k$} & \multirow{2}{*}{weight} & \multicolumn{2}{|c|}{accuracy} & \multicolumn{2}{|c|}{recall} \\
                & & avg. perform. & std. & avg. perform. & std. \\
                \hline
                $3$ & distance & $0.979$ & $0.013$ & $0.957$ & $0.039$\\
                \hline
                $5$ & distance & $0.982$ & $0.011$ &$0.957$ & $0.039$\\
                \hline
                $5$ & uniform & $0.982$ & $0.011$ & $0.957$ & $0.039$\\
                \hline
                $11$ & uniform & $0.975$ & $0.014$ & $0.927$ & $0.041$ \\
                \hline
                $21$ & uniform & $0.9719$ & $0.0179$ & $0.9168$ & $0.0533$ \\
                \hline
                $51$ & distance & $0.9404$ & $0.0238$ & $0.8342$ & $0.0664$
            \end{tabular}
            \caption{Results of $k$-NN for breast cancer dataset via cross-validation}
            \label{tbl:kNN_breast-cancer_cross-validation}
        \end{table}

        One can see that in our split using small values for $k$ yields to better results considering the accuracy or the recall and that using a weight function makes hardly a difference for both performance measures. Also the standard deviation is for both measures very small, which is good.

        The runtime for the classification is $0.002$, so a fraction of a second. Furthermore, we do not need to build a classifier. Hence, this algorithm runs very fast, especially because of the comparatively small $k$ values and the relatively small dataset.

        The results for the holdout method can be seen in Table~\ref{tbl:kNN_breast-cancer-holdout}. As we have only one split the standard deviation is for the accuracy as well as the recall always equal to $0$.

        \begin{table}[h]
        \centering
            \begin{tabular}[h]{r|c|c|c|c|c|}
               \multirow{2}{*}{$k$} & \multirow{2}{*}{weight} & \multicolumn{2}{|c|}{accuracy} & \multicolumn{2}{|c|}{recall} \\
                & & perform. & std. & perform. & std. \\
                \hline
                $3$ & distance & $0.9444$ & $0.0$ & $0.8519$ & $0.0$ \\
                \hline
                $5$ & distance & $0.9444$ & $0.0$ & $0.851$ & $0.0$ \\
                \hline
                $5$ & uniform & $0.9444$ & $0.0$ & $0.851$ & $0.0$ \\
                \hline
                $11$ & uniform & $0.9444$ & $0.0$ & $0.851$ & $0.0$ \\
                \hline
                $21$ & uniform & $0.9306$ & $0.0$ & $0.815$ & $0.0$ \\
                \hline
                $51$ & distance & $0.9167$ & $0.0$ & $0.778$ & $0.0$
            \end{tabular}
            \caption{Results of $k$-NN for breast cancer dataset via holdout}
            \label{tbl:kNN_breast-cancer-holdout}
        \end{table}

        Via the holdout method we obtained similar results for different parameter settings. Thus, one could conclude that the algorithm is not sensitive to different parameter settings. But this must not be necessarily true as the holdout method tests only on one split. As we have seen in the cross-validation method varying the parameters did change the optimality of the classifier, but the differences were not very big.

        Because the standard value of $k=5$ performed best in our cross-validation tests and was also one of the best values in the holdout method, we used it for the Kaggle competition. Using $k=5$ with uniform weights we received a $1.0$ score on the public leaderboard. We also tried different values for $k$ and used the distance as weight function but could obviously could not obtain a better value than the perfect score as for $k=5$, which was consistent with the results above.

    \subsection{Decision Tree}
        In this algorithm scaling is not needed as we do not need to measure the distance between samples. For building a decision tree we can change multiple parameters, e.g. the maximum depth of the tree or the criterion to measure the quality of a split which could be 'gini' or 'entropy'.

        \begin{table}[h!]
            \centering
            \begin{tabular}[h]{l|c|c|c|c|c|}
                \multirow{2}{*}{criterion} & \multirow{2}{*}{max. depth} & \multicolumn{2}{|c|}{accuracy} & \multicolumn{2}{|c|}{recall} \\
                & & avg. perform. & std. & avg. perform. & std. \\
                \hline
                entropy &$4$ & $0.951$ & $0.034$ &$0.937$ & $0.051$\\
                \hline
                gini & $5$ & $0.975$ & $0.014$ & $0.937$ & $0.077$\\\hline
                entropy & $5$ & $0.954$ & $0.017$ & $0.907$ &$0.081$\\\hline
                gini & $8$ & $0.958$  & $0.029$ & $0.969$ & $0.025$\\
                \hline
                entropy & $9$ & $0.958$ & $0.029$ & $0.958$ & $0.039$\\
                \hline
                gini & $9$ & $0.964$ & $0.025$ & $0.937$ & $0.077$
            \end{tabular}
            \caption{Results of decision tree for breast cancer dataset via cross-validation}
            \label{tbl:decision-tree_breast-cancer_cross-validation}
        \end{table}
        Table~\ref{tbl:decision-tree_breast-cancer_cross-validation} shows the average performance of accuracy and recall with the respective standard deviations of some of the parameter settings evaluated via cross-validation. 
        From these tests we can conclude the following. Considering the accuracy 'gini' performed for different tree lengths better as a splitting criterion than 'entropy', whereby performing best for a maximum depth of $5$. Measuring the recall both criterion performed rather similarly, with the best recall value being for 'gini' and a maximum depth of $8$. It should be noted that considering the recall 'gini' is not always better than 'entropy'. Hence, we can not state optimal parameter settings like for $k$-NN, since the standard deviations for the respective settings are comparatively small.

        We also evaluated the decision trees using the holdout method. Table~\ref{tbl:decision-tree_breast-cancer_holdout} shows the results. Like for the previous algorithm the standard deviation is equal to $0$ for both performance measures as we are only considering one split of the data. Hence, we did not include it in the table.

        \begin{table}[h!]
            \centering
            \begin{tabular}[h]{l|c|c|c|}
                criterion & max. depth & accuracy & recall \\
                \hline
                entropy &$4$ & $0.958$ & $0.889$\\
                \hline
                gini & $5$ & $0.958$ & $0.926$\\\hline
                entropy & $5$ & $1$ & $1$\\\hline
                gini & $8$ & $0.958$ & $0.963$\\
                \hline
                entropy & $9$ & $0.972$ & $0.926$\\
                \hline
                gini & $9$ & $0.972$ & $0.926$\\
            \end{tabular}
            \caption{Results of decision tree for the breast cancer dataset via holdout}
            \label{tbl:decision-tree_breast-cancer_holdout}
        \end{table}

        We can see that the holdout method returned a perfect classifier with full accuracy and recall for the corresponding split with 'entropy' as criterion a maximum depth of $5$. Compared with the results of cross-validation this was not one of the optimal settings. For this method 'entropy' performed in general a bit better than 'gini' resp.\ not worse.

        Since the holdout method evaluates only on one training/test split, the results depend only on the quality of this single split. Via cross-validation we train using multiple splits, whereby we can balance the quality. This is the reason why we will document only the results obtained by cross-validation for the following classifiers resp.\ datasets. However, we will remark major differences between these two methods, if we observe any.

        After these tests we can see that on the given dataset changing different parameter settings in the decision tree algorithm did change the scores of the classifier, but the differences were not really big. However, there were apparent differences between the holdout and the cross-validation testing. Considering the results of cross-validation, as this is less dependent of the quality of one single split, the differences of accuracy resp. recall is rather small. Hence, we can conclude that it is not very sensitive to different parameter settings for this dataset.

        Using the best parameter settings of our testing we submitted it to the Kaggle competition. However, the best score on the public leaderboard was still worse than the results from $k$-NN. We reasoned that the cause for the comparatively bad results in Kaggle was that $k$-NN was simply better suited for this dataset.

        %Not limiting the depth of the decision tree gave us a depth of $7$ on the learning set, which is not high considering the dimension of $32$ and the size of the test set. Therefore, we did not limit the depth of the decision tree as it did not seem to be overfitted. Since the first result was only $0.92307$, which compared to the $k$-NN classifier was quite bad we decided to set the splitter to random to see whether the results changed. The result was slightly better but that might have been luck rather than an actually better tree. Using the entropy instead of the gini impurity to measure the quality of a split, we obtained slightly better results, but there was still room for improvement.

%    \subsection{Perceptron}
%       Surprisingly the perceptron classifier performed well on the public leaderboard giving a score of $1.0$ like $k$-NN at the first try. Changing the maximum number of iterations as well as $\alpha$ did not change the result of the perceptron, which implied that the perceptron converged to a stable state.

    \subsection{Random Forest}
        Changing the parameter values described in Section~\ref{subsec:random-forest} provided a lot of information. We decided to document the results of accuracy and recall for different numbers of trees and weights associated with the classes, which can be seen in Figure~\ref{fig:breast-cancer_random-forest}. For the other parameters in the algorithm we considered the default values.

        \begin{figure}[h!]
            \centering
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_1/paper/figures/breast-cancer-accuracy-random_forest.png}
                \caption{Accuracy}
                \label{fig:breast-cancer_random-forest_accuracy}
            \end{subfigure}
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_1/paper/figures/breast-cancer-recall-random_forest.png}
                \caption{Recall}
                \label{fig:breast-cancer_random-forest_recall}
            \end{subfigure}
            \caption{Performance measures of random forest for breast cancer dataset}
            \label{fig:breast-cancer_random-forest}
        \end{figure}

        In Figure~\ref{fig:breast-cancer_random-forest_accuracy} the performance of 'balanced' and 'balanced\_subsample' is almost identical, independent of the number of trees. The difference between these two settings is that the weights are computed based on the bootstrap sample for every tree grown and not on the whole dataset. Additionally, one can see that uniform weights performed the best, except for a small number of trees, with a peek at $100$ trees.

        The recall however improved with a higher number of trees for 'uniform' and 'balanced\_subsample' class weights. Whereas with a 'balanced' class weight the measure decreased between a number of $100$ and $1\,000$ trees, which can be seen in Figure~\ref{fig:breast-cancer_random-forest_recall}.

        For this algorithm we did a parameter search on the random forest algorithm for the number of trees, the maximum depth of the tree, the criterion to measure the quality of a split and some other parameters. We obtained the following: 
        \begin{itemize}
            \item Number of trees: $10\,000$
            \item Maximum depth of a tree: None
            \item Minimum number of samples required to split an internal node: $5$
            \item Minimum number of samples required to be at a leaf node: $1$
            \item Number of features to consider when looking for the best split: 'sqrt'
            \item Bootstrap samples are used when building tree: False
            \item Weights associated with classes: 'balanced\_subsample'
        \end{itemize}

        The obtained parameters were interesting because of various aspects. First, the treedepth was unlimited, which one would expect to be a possible cause of overfitting. Second, bootstrapping the samples for tree generation was turned off and as class weight 'balanced\_subsample' was used, which is interesting, since this class weight function calculates the weights inversly proportional to the class frequencies in the input data, but based on the subsample of a bootstrapped tree. As the trees are not bootstrapped every feature is used for every tree generation and therefore 'balanced\_subsample' should be equal to 'balanced'. We suspect that it actually is, but share the first place on the parameter search, so only one of those parameter options is returned.

        Next, we submitted the classifier learned with the obtained parameters to the Kaggle competition which resulted in a score of $0.96$ on the public test set. This was pretty good, especially compared with the decision tree approach. However, it was still not as good as the the $k$-NN classifier.

        As stated in Section~\ref{subsec:random-forest} a big disadvantage of this algorithm is its runtime. Compared with $k$-NN and decision tree, which have a runtime of at most few seconds, this algorithm needs about $20$ seconds to compute the best classifier with $10\,000$ trees.

\section{Amazon Commerce Reviews}
    For this problem a dataset with $10\,000$ numeric attributes with integer values was given. Figure~\ref{fig:amazon_value_ranges} shows a boxplot diagramm of the value ranges of the attributes of the $749$ samples in the dataset. It can be seen that the range of most of the features is less than 10, but we also have some attributes with a big range.

    \begin{figure}[h!]
        \centering
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=1\textwidth]{exercise_1/paper/figures/amazon_classes_range_plot.png}
            \caption{Boxplot of the values ranges of the attributes}
            \label{fig:amazon_value_ranges}
        \end{subfigure}
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=1\textwidth]{figures/amazon_classes_bar.png}
            \caption{Class distribution}
            \label{fig:amazon_classes_bar}
        \end{subfigure}
        \caption{Figures for the Amazon Commerce Review dataset}
        \label{fig:amazon}
    \end{figure}

    Based on these attributes the aim was to predict a nominal feature with $50$ possible values, namely who submitted a review. The distribution of the classes is not uniform, as this would mean that for each class there are about $15$ samples in our dataset which is not the case. Figure~\ref{fig:amazon_classes_bar} shows on the $x$-axis the number of samples in a class and on the $y$-axis the number of classes with the corresponding number of samples, e.g. there are 3 classes, each with 10 samples of the dataset. It can be seen that the distribution is not uniform and about half of the classes have a sample size per class between $16$ and $18$.

    Because we do not have a binary decision problem, the performance measures recall and precision are rather meaningless. One could look at the accuracy per class, but as the classes were all roughly the same size we decided to forgo this.

    \subsection{$k$-NN}
        For this dataset we first learned some classifiers and submitted it to the Kaggle competition before evaluating it locally on the given dataset.

        We run the $k$-NN algorithm with different values for $k$. 
        First, we normalised the data using the min-max-scaling and tried $k=5$, since this was the default value in scikit-learn, which led to a very good result in the Breast Cancer dataset. Unfortunately, we obtained a very bad result of $0.05$. Our next attempts with higher values for $k$ did not yield to an improvement. Finally, we tried $k=1$ which improved the result to $0.12$.

        Next, we submitted a classifier trained on the original data, i.e. without scaling the variables and setting the distance as weight function. With these setting we obtained better scores, namely $0.216$ for $k=1$ and $0.267$ for $k=5$.

        Apparently, we could not obtain good results with this approach since the number of submissions per day was limited. Hence, we tried to find optimal parameter values locally before submitting it to the competition. Again, we evaluated different classifiers via cross-validation resp.\ the holdout method. Table~\ref{tbl:kNN_amazon_cross-validation} shows the results of $k$-NN classifiers using some different settings for $k$, the weight function and the scaling method.

        \begin{table}[h!]
        \centering
            \begin{tabular}[h]{r|c|c|c|c}
                $k$ & weight & scaling & avg. accuracy & std.\\
                \hline
                $1$ & arbitrary & no & $0.2667$ & $0.0337$ \\
                \hline
                $1$ & arbitrary & min-max & $0.1227$ & $0.0275$ \\
                \hline
                $3$ & uniform & min-max & $0.0747$ & $0.0122$ \\
                \hline
                $3$ & distance & standard & $0.0653$ & $0.154$ \\
                \hline
                $5$ & distance & no & $0.2507$ & $0.326$ \\
                \hline
                $5$ & distance & min-max & $0.1013$ & $0.0195$ \\
                \hline
                $11$ & uniform & standard & $0.0293$ & $0.0068$ \\
                \hline
                $11$ & uniform & no & $0.2093$ & $0.0108$
            \end{tabular}
            \caption{Results of $k$-NN for Amazon reviews dataset via cross-validation}
            \label{tbl:kNN_amazon_cross-validation}
        \end{table}

        One can see that the difference between the min-max scaler and the standard scaler is rather small. Whereas without scaling the obtained classifiers are much better, even for different $k$ values. From our tests we can conclude that without scaling the attributes, considering the first nearest neighbor is the best prediction we can make with the $k$-NN algorithm. Nevertheless, with an accuracy of $0.2667$ this is still not good enough.

        The average runtime of this algorithm is about $1$ second, which is very fast but compared with the breast cancer dataset much slower. The reason behind this is the size of the dataset and the number of attributes as both of these numbers are higher compared to the breast cancer dataset. 
        %avg runtime: $1.0795$ seconds

        Although we tried different parameters for this algorithm, the classifiers still performed poorly. We think the reason for this is because of the high number of attributes and a comparatively low number of samples.

    %\subsection{Perceptron}
      %  Another approach was using a multilayer perceptron. The resulting classifier performed only slightly better than $k$-NN with a score of about $0.075$.
       % We think that the test data is not linear separable, and therefore a simple perceptron is not the way to go.
        %\todo[inline]{Reasoning: same as above?}
        %\todo[inline]{different parameters like max number of iterations or alpha?}

    \subsection{Decision Tree}
        As we could change many different parameters to obtain a better classifier, we decided to split our data first and then evaluate the classifiers on the test set before submitting it to the Kaggle competition. The results of the cross-validation method with different parameter settings can be seen in Table~\ref{tbl:decision-tree_amazon_cross-validation}. Furthermore, this algorithm had an average running time of $2.2$ seconds, which is slower than $k$-NN.

        %A decision tree with unbounded depth and the default values of scikit-learn instantly performed better than the default values of $k$-NN with a score of $0.189$. Limiting the maximal depth however did not yield to greatly different results.

        %As we could change many different parameters to obtain a better classifier, we decided to split our data into a $75\%$ training and $25\%$ test set and evaluate the classifiers first on the test set before submitting it to the Kaggle competition. The results of this holdout method can be seen in Table~\ref{tbl:decision-tree_amazon}. Additionally, we also tested different parameters classifiers via cross-validation, where the results can also be seen in Table~\ref{tbl:decision-tree_amazon_cross-validation}.

        \begin{table}[h!]
            \centering
            \begin{tabular}[h]{l|c|c|c}
                criterion & max. depth & avg. accuracy & std. \\
                \hline
                gini & 5 & $0.124$ & $0.009$ \\
                \hline
                entropy & 7 & $0.2053$ & $0.0351$ \\
                \hline
                gini & 7 & $0.1467$ & $0.0112$ \\
                \hline
                gini & 11 & $0.2173$ & $0.0371$ \\
                \hline
                entropy & 11 & $0.204$ & $0.0209$ \\
                \hline
                entropy & 17 & $0.1907$ & $0.0241$
            \end{tabular}
            \caption{Results of decision tree for Amazon reviews dataset via cross-validation}
            \label{tbl:decision-tree_amazon_cross-validation}
        \end{table}

        In general, 'entropy' performed better than 'gini' as criterion but the standard deviation was also a bit higher. Also limiting the maximum depth of the tree resulted in a better classifier.

        Based on these results, we picked a few parameter setting and submitted the corresponding classifiers to Kaggle. But we did not expect to get a great score which was the case, as also our evaluation did not yield a good result. Hence, we decided to focus on a random forest instead.

    \subsection{Random Forest}
        Using the random forest algorithm for training the classifier turned out to be a lot more successful than our previous attempts.

        %First, we trained $10\,000$ trees and got a result of $0.752$ in the public leaderboard. A big leap in quality. Our tests showed that using 'gini' to measure the quality of a split yielded better results than 'entropy'. That is why we only considered 'gini' as criterion.

        We still tested the classifiers locally on the given training set. Our tests showed that using 'gini' to measure the quality of a split yielded better results than 'entropy'. That is why we only considered 'gini' as criterion. Also a high number of trees improved the classifier. We were optimistic that this algorithm would return a better classifier than $k$-NN and decision tree, as the best obtained accuracy was $0.7227$.

        After some tests we did a parameter search on the number of trees, tree depth and some more parameters of the random forest algorithm. From this we obtained the following values:
        \begin{itemize}
            \item Number of trees: $10\,000$
            \item Maximum depth of a tree: $50$
            \item Minimum number of samples required to split an internal node: $5$
            \item Minimum number of samples required to be at a leaf node: $1$
            \item Number of features to consider when looking for the best split: 'sqrt'
            \item Bootstrap samples are used when building tree: False
        \end{itemize}

        The trained classifier with these parameters obtained a score of $0.755$ in the Kaggle competition. Since the distribution of classes is not uniform in the given dataset, we also tried assigning weights to the classes dependent on the class frequencies. This yielded a slightly better result of $0.757$, but as this is the score only for the public test set in Kaggle, we cannot say for sure that it is really an improvement.

        A disadvantage of this algorithm is its runtime since this increases noticeably with the number of trees, e.g. for $3\,000$ trees the running time is about $40$ seconds.

\section{Spambase}
    This dataset contains various information about mails, e.g.\ the frequency of words or capital letters, the length of sequences of capital letters in the mail and the appearence of specific words. All of the given attributes are integer or real values. Figure~\ref{fig:spambase_value_ranges} shows a boxplot diagram of the value ranges of all attributes in the Spambase dataset. We can see that the median is 10 but the value ranges vary a lot as we also have outliers with a range of more than $10\,000$. There are no missing values and with a sample size of about $4\,600$ and $58$ attributes this is a rather large and high dimensional dataset compared to the following dataset Credit Approval.

    The task is to classify a certain mail as spam (true) or not spam (false) based on the given features. The distribution of the two possible classes of this dataset is shown in Figure~\ref{fig:spambase_classes_pie}.

    \begin{figure}[h!]
        \centering
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=1\textwidth]{figures/spambase_range_plot.png}
            \caption{Boxplot of the values ranges of the attributes}
            \label{fig:spambase_value_ranges}
        \end{subfigure}
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=1.1\textwidth]{exercise_1/paper/figures/spambase_positive_pie.png}
            \caption{Class distribution}
            \label{fig:spambase_classes_pie}
        \end{subfigure}
        \caption{Figures for the Spambase dataset}
        \label{fig:spambase}
    \end{figure}

    \subsection{$k$-NN}
        In Figure~\ref{fig:k-NN_spambase} we have compiled two graphs describing how growing $k$ values and different weight functions affect the average performance of $k$-NN, testing it via cross-validation.

        As one can see in the Figures~\ref{fig:k-NN_spambase_accurracy} and \ref{fig:k-NN_spambase_precision} the parameters affect precision and accuracy very differently. While the precision steadily grows for both weight functions with increasing $k$, the accuracy for uniform weights decreases for bigger $k$ values strongly starting at $k\approx 15$. In general distance based weights improve accuracy and precision and are less effected by growing $k$ values.
        The stronger drop of uniform weights makes sense, since far away points might skew the results. The reason for rising precision with rising $k$ could be that all the instances that are classified as spam are grouped closely together while the instances not classified as spam are spread farther in the distance.

        \begin{figure}[h!]
            \centering
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_1/paper/figures/spambase-accuracy-kNN.png}
                \caption{Accuracy}
                \label{fig:k-NN_spambase_accurracy}
            \end{subfigure}
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_1/paper/figures/spambase-precision-kNN.png}
                \caption{Precision}
                \label{fig:k-NN_spambase_precision}
            \end{subfigure}
            \caption{Performance measures for $k$-NN}
            \label{fig:k-NN_spambase}
        \end{figure}

        As the attributes have very different value ranges scaling was needed. We tried the min-max-scaler and the standard-scaler of scikit-learn and obtained better results by the latter, i.e.\ converting the mean of every attribute to 0 and the standard deviation to 1. Moreover, by using the distance as weight function the results could be improved a little bit more.

        For finding the optimal parameters to use in the $k$-NN algorithm we did a parameter search which returned $k=11$ as optimal value for the nearest neighbors algorithm. Additionally, we chose to use the Euclidean metric to calculate the distance between nodes. We tried using uniform weights for all neighbours, but came to the result that ranking them by their inverse distance gave us better results.

        We tested our classifier by comparing it to classifiers obtained by changing the parameters. As we would like to predict a binary attribute, we tried some different odd values for $k$ to ensure the optimality of this parameter. Furthermore, we tried to uniformly distribute the weights and using different distance metrices. But the classifier built with the parameters from the parameter search was the best resulting a score of $0.9227$.

   % \subsection{Perceptron}
        %In the multilayer perceptron algorithm of scikit-learn we decided to vary the following parameters to optimize our classifier:
       % \begin{itemize}
          %  \item Maximum number of iterations
          %  \item Learning rate $alpha$
          %  \item solver = ['lbfgs', 'sgd', 'adam'] for optimizing the weights
       % \end{itemize}
       % We obtained the following: the maximum number of iterations does not have an impact on the classifier for big values, i.e. $1000$ iterations are enough. Moreover, with the default value for $alpha=0.0001$ we had a better classifier. Additionally, the stochastic gradient descent solver did better than the optimizer in the family of quasi-Newton methods 'lbfgs' and the default solver 'adam'.

       % With these parameters we determined a classifier with an accuracy of $0.9392$. Hence, we could improve the classifier obtained by the $k$-NN algorithm. For us this means that the dataset is almost linearly separable.

    \subsection{Decision Tree}
        In Figure~\ref{fig:decision-tree_spambase} we compared the two criterion 'gini' and 'entropy' with respect to accuracy and precision. One can see that the performance highly depends on the maximum tree depth. For both performance measures the parameter setting with the best result is 'entropy' with a maximum tree depth of $8$. Limiting the length of a tree is very important, as seen in Figure~\ref{fig:decision-tree_spambase_precision}, as the precision is decreasing for growing tree depth. The reason for this is probably overfitting the decision tree to the training set. Moreover, our tests revealed using 'best' as splitter provides a bit better classifier than 'random'.

        \begin{figure}[h!]
            \centering
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1.1\textwidth]{exercise_1/paper/figures/spambase-accuracy-decision_tree.png}
                \caption{Accuracy}
                \label{fig:decision-tree_spambase_accurracy}
            \end{subfigure}
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_1/paper/figures/spambase-precision-decision_tree.png}
                \caption{Precision}
                \label{fig:decision-tree_spambase_precision}
            \end{subfigure}
            \caption{Performance measures for decision tree }
            \label{fig:decision-tree_spambase}
        \end{figure}

        Using the best parameter settings we obtain a decision tree with an average accuracy of $0.91$, which is pretty good but still a bit worse than the previous classifier.

    \subsection{Random Forest}
        For this algorithm we once again did a parameter search to find optimal values for several parameters which were the following:
        \begin{itemize}
                \item Number of trees: $10\,000$
                \item Maximum depth of a tree: None
                \item Minimum number of samples required to split an internal node: $2$
                \item Minimum number of samples required to be at a leaf node: $1$
                \item Number of features to consider when looking for the best split: 'sqrt'
                \item Bootstrap samples are used when building tree: True
        \end{itemize}
        The random forest classifier learned with these parameter settings led to an average accuracy of $0.96$ via cross-validation. We also varied the parameter values but could not increase the performance.

\section{Credit Approval}
    This dataset is rather small compared to the previous dataset Spambase with only $690$ instances and $15$ attributes. It aims to predict whether a credit card application will be approved (true) or not (false) based on several categorical and continuous features. Figure~\ref{fig:credit-approval_classes_pie} shows the distribution of the classes in the given dataset. The two classes are not equally distributed, since there are more cases where the application is denied. 
    Although the proportion of True to False is not 1:1, there are still many cases where the credit card application is approved.
    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.5\textwidth]{exercise_1/paper/figures/credit_approval_pie.png}
        \caption{Class distribution}
        \label{fig:credit-approval_classes_pie}
    \end{figure}

    The Credit Approval dataset is interesting because of many factors. First, it has nominal as well as numeric attributes. The previous dataset 'Spambase' did not contain any nominal attributes except the predicted class. Figure~\ref{fig:credit-approval_attributes} shows some properties of the attributes in our dataset. A boxplot diagram of the value ranges of the numeric attributes can be seen in Figure~\ref{fig:credit-approval_numeric-attributes}, whereas the number of possible values of categorical attributes can be found in Figure~\ref{fig:credit-approval_categorical_attributes}. The diagrams show that the value ranges of both types of attributes are widely spread. We have numeric features with a range of $15$ but also one with a range of almost $100\,000$. But also the number of possible values for the nominal attributes varies between $2$ to $14$.

    \begin{figure}[h!]
        \centering
        \begin{subfigure}[c]{0.4\textwidth}
            \centering
            \includegraphics[width=1\textwidth]{exercise_1/paper/figures/credit_approval_continous_range_plot.png}
            \caption{Boxplot of the values ranges of the numeric attributes}
            \label{fig:credit-approval_numeric-attributes}
        \end{subfigure}
        \begin{subfigure}[c]{0.5\textwidth}
            \centering
            \includegraphics[width=1.1\textwidth]{exercise_1/paper/figures/credit_approval_categories_bar.png}
            \caption{Number of possible values for categorical attributes}
            \label{fig:credit-approval_categorical_attributes}
        \end{subfigure}
        \caption{Features of Credit Approval dataset}
        \label{fig:credit-approval_attributes}
    \end{figure}

    Moreover, the Credit Approval dataset also contains missing values. About $5\%$ of the instances have some missing values. We decided to impute the values in different ways and see how it affects the performance of the classifiers. We univariately estimated the values by the mean, median resp. the most frequent value. As the true und false classes were roughly the same size we chose to only look at the accuracy for this dataset.

    \subsection{$k$-NN}
        For $k$-NN the first question was obviously how to translate the nominal values to numeric values in order to measure a distance. For this we decided for binary nominal attributes to assign either $0$ or $1$. For the remaining categorical attributes we used one hot encoding. 
        Next, we normalised the numeric values via the integrated min-max resp.\ normalised scaler and run $k$-NN algorithm.

        \begin{figure}[h!]
            \centering
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_1/paper/figures/credit-approval-accuracy-kNN_uniform.png}
                \caption{Uniform weights}
                \label{fig:k-NN_credit-approval_uniform}
            \end{subfigure}
            \begin{subfigure}[c]{0.45\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_1/paper/figures/credit-approval-accuracy-kNN_distance.png}
                \caption{Distance-based weights}
                \label{fig:k-NN_credit-approval_distance}
            \end{subfigure}
            \caption{Comparision of imputation methods}
            \label{fig:k-NN_credit-approval}
        \end{figure}

        For missing values we had different approaches which can be seen in Figure~\ref{fig:k-NN_credit-approval}. This includes substituting missing values of a categorical attribute with the most frequent one or with a constant, which stands for a missing value, i.e. we are adding a new value to the attribute. Missing values of numeric attributes are replaced with the median, the mean or the most frequent one. Our tests showed that using the median or the mean value makes no difference. This is the reason why we omitted the approach with the mean value.

        As one can see in Figure~\ref{fig:k-NN_credit-approval} the differences between the different imputation methods were negligible. One reason for this is probably the comparatively small amount of missing values in the dataset.
        It is also apparent from the graph that the uniform weights performed better than the distance-based weights for lower $k$ values. The reason for higher $k$ values still having a good performance could be that instances that are classified the same are grouped together rather closely.

        Again, we did a parameter search to determine the best values, which returned $k=35$. By using a simple imputation which replaces each missing value by the median, we got an accuracy of 
        $0.849$ for this $k$ value. Using the most frequent value in the imputation led to a minimal drop of accuracy to $0.843$. Without scaling the accuracy dropped to $0.67$. Additionally, we tried different values for $k$ which led to worse results. Using min-max scaling instead of the normalised scaling had no impact on the results.

        We also tried to impute the missing values by simply assigning the most frequent value of the attribute or inserting a new "missing" category and afterwards one hot encoding it. This led to an optimal parameter $k=37$ and the best accuracy of $0.855$. Changing between uniform weight and weights based on distance made a negligible difference.

   % \subsection{Multilayer Perceptron}
      % Perceptron with the maximal number of iterations being $100000$ and $\alpha=10^{-5}$ led to an accuracy of $0.8$.
       %\todo[inline]{other values}

    \subsection{Decision Tree}
        As one can see the imputation method had greater influence on the decision tree model, than the $k$-NN model. This could be due to the fact that while a single wrongly approximated attribute does not greatly change the distance between two instances, it could lead to the instance being put down a whole other path on the decision tree and therefore lead to a wrong result.

        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.6\textwidth]{exercise_1/paper/figures/credit-approval-accuracy-decision_tree.png}
            \caption{Influence of imputation on accuracy}
            \label{fig:credit-approval_decision_tree}
        \end{figure}

        In order to determine which parameters would lead to an optimal decision tree we once again did a parameter search, which gave us the following parameter settings, which are consistent with the figures above. Use 'gini' to measure the quality of a split, limit the maximum tree depth to $5$ and 'random' as strategy to choose the split at each node. Using these parameters the learned classifier had an accuracy of $0.832$.

    \subsection{Random Forest}
        Like for the previous classifiers we evaluated different parameter settings and then confirmed the obtained results with a parameter search. We obtained the following optimised parameter settings:
        \begin{itemize}
            \item Number of trees: $10\,000$
            \item Maximum depth of a tree: $50$
            \item Minimum number of samples required to split an internal node: $5$
            \item Minimum number of samples required to be at a leaf node: $1$
            \item Bootstrap samples are used when building tree: True
        \end{itemize}

        The corresponding built classifier led to an accuracy of $0.862$. This was the best value which we could achieve as we also tested it with other parameter settings but could not improve this. Comparing this result with the classifiers of the previous of this dataset this has a slightly better accuracy, hence slightly better.

        %parameter search: parameters
            %'randomforestclassifier__max_features': 'sqrt', 'randomforestclassifier__class_weight': 'balanced_subsample'

\section{Conclusions}
    Summing up we can say, that in general there is no algorithm building a classifier that could predict the respective attribute perfectly in each case for every dataset. In particular, there is not even an algorithm that is optimal for each dataset as we could see from the results.

    Although the classifiers returned from the random forest algorithm were mostly pretty good and in many cases even the best, it was outperformed by $k$-NN in the Breast Cancer dataset. Although $k$-NN had a perfect result for the Breast Cancer dataset in the public split of Kaggle, it failed at classifying the more complex dataset Amazon.

    $k$-NN and decision tree where both rather sensitive on big changes of the parameters for the algorithm, however random forest was not. The reason for this is probably that the random forest algorithm builds its classifier by taking the average of a specified of number decision trees.

    The longest runtime of all algorithms had random forest for all datasets, especially for the Amazon review dataset. The runtime of this algorithm increased in particular for huge tree sizes, which however generally performed better on this dataset. This proved very problematic for the parameter searches, which could not be performed within a reasonable time frame for higher number of trees. Figure~\ref{fig:runtime-comparison} shows the runtime in seconds of the random forest algorithm for constructing a classifier using $1\,000$ decision trees. It shows that the runtime also depends on the number of samples and number of features, not only on the parameters.

    \begin{figure}[h!]
            \centering
            \includegraphics[width=0.55\textwidth]{exercise_1/paper/figures/runtime_comparison.png}
            \caption{Runtime comparison of different classification algorithms}
            \label{fig:runtime-comparison}
    \end{figure}

\end{document}

### 2021-02-20 exercise_2/presentation/Presentation_P2.tex
Add files via upload

\documentclass[10pt]{beamer}

\usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}
\usepackage{xspace}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{multirow}

\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\w}{\vec{\textbf{w}}}
\newcommand{\costder}{\frac{\partial MSE}{\partial w_j}(\w)}
\newcommand{\R}{\mathbb{R}}

\title{Machine Learning - Exercise 2}
\subtitle{Regression}
% \date{\today}
\date{}
\author{Esra Ceylan, Daniel Fangl, Christian Hatschka}
\institute{TU Wien}
% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}

\begin{document}
\maketitle

\begin{frame}{Table of contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents%[hideallsubsections]
\end{frame}

\section[Data Sets]{Data Sets}
    \begin{frame}[fragile]{Diamonds Data Set}
        Several attributes of diamonds, e.g. carat, clarity or measurements has been collected.

        \begin{itemize}
            \item \#samples = $ 53\,940$
            \item \#attributes = $9$
            \item $6$ numeric and $3$ categorical attributes
            \item No missing values
            \item To predict: price in US Dollars
        \end{itemize}
    \end{frame}

    \begin{frame}[fragile]{Concrete Data Set}
        Data set contains information about the composition as well as the age of cement in days and it's compressive strength.
        \begin{itemize}
            \item \#samples = $ 1\,030$
            \item \#attributes = $8$
            \item Only numeric attribute
            \item Has no missing values
            \item To predict: concrete compressive strength measured in MPa
        \end{itemize}
    \end{frame}

    \begin{frame}[fragile]{Life Expectancy Data Set}
        Data set contains health factors of 193 countries between the years $2000$ to $2015$.

        \begin{itemize}
            \item \#samples = $ 2\,938$
            \item \#attributes = $20$
            \item $19$ numeric attributes and $1$ categorical feature
            \item Has missing values
            \item To predict: life expectancy in years
        \end{itemize}
    \end{frame}

\section[Data Preparation]{Data Preparation}
    \begin{frame}[fragile]{Data Preparation}
        \begin{enumerate}
            \item Categorical data:
                \begin{itemize}
                    \item One-hot encoding
                \end{itemize}

            \item Missing values:
                \begin{itemize}
                    \item Most common value
                    \item Median
                \end{itemize}

            \item Scaling:
                \begin{itemize}
                    \item Without
                    \item Standard-Scaler 
                    \item Min-Max-Scaler
                \end{itemize}
        \end{enumerate}
    \end{frame}

\section[Gradient Descent]{Gradient Descent Algorithm}
    \begin{frame}[fragile]{Gradient Descent}
        \begin{itemize}
            \item $n=\#attributes$
            \item Weight vector $\w = (w_0, ..., w_n)'$
            \item Minimize error by computing impact of all $w_j$:
                \begin{align*}
                    \min MSE(\w) &= \min \frac{1}{\#samples} RSS(\w) \\
                    &= \min \frac{1}{\#samples} \sum_{i=1}^{\#samples}(y_i - (w_0 + \sum_{j=1}^{n}w_{j} x_{ij}))^2
                \end{align*}
                Use $MSE$ instead of $RSS$ as cost function because even for different values for $\alpha$ the weights do not converge for data set with big sample size
        \end{itemize}
    \end{frame}

    \begin{frame}[fragile]{Gradient Descent: Pseudocode}
        \begin{algorithm}[H]
            \caption{GD-Regressor($\alpha$, $max\textunderscore iterations$, $X_{t}$, $Y_{t}$)}
			\begin{algorithmic}[1]
			    \For{$j=0$ to $n$} 
			    \Comment Initialize weights
			        \State $w_j=1$ 
			    \EndFor
				\For{$k = 1$ to $max\textunderscore iterations$}
    				\For{$j=0$ to $n$}
    				\Comment Calculate derivative
    				    \State Calculate $\costder$
    				\EndFor
    				\For{$j=0$ to $n$}
    				\Comment Update weights
    				    \State $w_j = w_j - \alpha \costder$
    				\EndFor
				\EndFor
				\State \Return $\w$
			\end{algorithmic}
		\end{algorithm}
    \end{frame}

    \begin{frame}[fragile]{Calculating Partial Derivative}
        \begin{enumerate}
            \item Manually calculated:
                \begin{align*}
                    \costder = \left\{
                    	\begin{array}{ll}
                    		\frac{-2}{\#samples} \sum_{i=1}^{\#samples}(y_i - (w_0 + \sum_{j=1}^{n}w_{j} x_{ij})), & j=0, \\
                    		\frac{-2}{\#samples} \sum_{i=1}^{\#samples}(y_i - (w_0 + \sum_{j=1}^{n}w_{j} x_{ij}))\cdot x_{ik},  & j \geq 1.
                    	\end{array}
                    \right.
                \end{align*}
                $\rightarrow$ too slow because of huge number of arithmetic operations $\sim 2n \cdot \#samples$.

            \item In terms of vector-operations:

                $\Tilde{X_t} \in \R^{\#samples \times (n+1)}$...insert first column with $1$ to training set $X_t$

                \begin{align*}
                    \left( \costder \right)_{j=0,...,n} = \frac{-2}{\#samples} \Tilde{X_t}' \cdot \left(Y_t - \Tilde{X_t} \cdot \w \right) 
                \end{align*}
                $\rightarrow$ much faster
        \end{enumerate}
    \end{frame}

    \begin{frame}[fragile]{Gradient Descent: Pseudocode Prediction}
        \begin{algorithm}[H]
            \caption{GD-Prediction($\w$, $X_p$)}
			\begin{algorithmic}[1]
			    \State $\Tilde{X_p}$ := insert first column with $1$ to $X_p$
			    \State $Y = \Tilde{X_p} \cdot \w$
			    \State \Return $Y$
			\end{algorithmic}
		\end{algorithm}
		Again, using vector operations made the prediction much faster.
    \end{frame}

    \begin{frame}{Results}
        \begin{itemize}
            \item Vector operations way faster than simply summing up
            \item Although very fast takes more iterations to reach similar results as in sklearn
            \item Weight initialization has an impact on iterations needed till convergence $\rightarrow$ done differently in sklearn

            \item For all our data sets best results using Standard-Scaling
            \item Min-Max-Scaler was not bad, but also not really good
            \item Without scaling weights get too big $\rightarrow$ do not converge

            \item In the following plots we used $\alpha=10^{-2}$ for our implementation of Gradient Descent (best $\alpha$ in our tests) and $\alpha=10^{-5}$ for the scikitlearn implementation
        \end{itemize}
    \end{frame}

    \begin{frame}{Performance on Diamonds Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_scores_mean_sq_err.png}
            \caption{Mean squared error of Gradient Descent on Diamonds Data Set}
            \label{fig:Grad_Diamond_MSE}
       \end{figure}
    \end{frame}

    \begin{frame}{Performance on Diamonds Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_scores_max_error.png}
            \caption{Max. error of Gradient Descent on Diamonds Data Set}
            \label{fig:Grad_Diamond_max-error}
       \end{figure}
    \end{frame}

    \begin{frame}{Performance on Concrete Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_gradient-descent_scores_mean_sq_err.png}
            \caption{Mean squared error of Gradient Descent on Concrete Set}
            \label{fig:Grad_Concrete_MSE}
       \end{figure}    
    \end{frame}

    \begin{frame}{Performance on Concrete Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_gradient-descent_scores_max_error.png}
            \caption{Max. error of Gradient Descent on Concrete Set}
            \label{fig:Grad_Concrete_max-error}
        \end{figure}        
    \end{frame}

    \begin{frame}{Performance on Life Expectancy Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_gradient-descent_scores_mean_sq_err.png}
            \caption{MSE of Gradient Descent on Life Expectancy Data Set}
            \label{fig:Grad_LE_MSE}
       \end{figure}    
    \end{frame}

    \begin{frame}{Performance on Life Expectancy Data Set}
          \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_gradient-descent_scores_max_error.png}
            \caption{Max. error of Gradient Descent on Life Expectancy Data Set}
            \label{fig:Grad_LE_max-error}
       \end{figure}
    \end{frame}

    \begin{frame}{Runtime on Diamonds Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_scores_runtime.png}
            \caption{Runtime of Gradient Descent on Diamonds Data Set}
            \label{fig:Grad_Diamond_runtime}
       \end{figure}
    \end{frame}

    \begin{frame}{Runtime on Concrete Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_gradient-descent_scores_runtime.png}
            \caption{Runtime of Gradient Descent on Concrete Data Set}
            \label{fig:Grad_Concrete_runtime}
       \end{figure}        
    \end{frame}

    \begin{frame}{Runtime on Life Expectancy Data Set}
          \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_gradient-descent_scores_runtime.png}
            \caption{Runtime of Gradient Descent on Life expectancy Data Set}
            \label{fig:Grad_LE_runtime}
       \end{figure}
    \end{frame}

\section[$k$-NN]{$k$-NN Algorithm}
    \begin{frame}[fragile]{$k$-NN}
        $n$ = \#attributes

        Distance functions (using numpy.linalg.norm in Python):
            \begin{enumerate}
                \item Manhattan distance: $d_1(x_1, x_2) = \sum_{i=1}^n |x_{1i} - x_{2i}|$
                \item Euclidean distance: $d_2(x_1, x_2) = \sqrt{\sum_{i=1}^n (x_{1i} - x_{2i})^2}$
                \item Chebyshev distance: $d_\infty(x_1, x_2) = \max_{i \in \{1,...,n\}}|x_{1i} - x_{2i}|$
            \end{enumerate}

        Weight:
            \begin{enumerate}
                \item Uniform $\rightarrow$ mean of predicted class of $k$ nearest neighbours
                \item Distance based: $\frac{1}{d(x_1, x_2)+\varepsilon}$ (very small $\varepsilon>0$ to prevent division by $0$) $\rightarrow$ weighted mean of predicted class of $k$ nearest neighbours
            \end{enumerate}
    \end{frame}

    \begin{frame}[fragile]{$k$-NN: Pseudocode}
        \begin{algorithm}[H]
            \caption{$k$-NN-Regressor($k$, distance-fct $d$, weight, $X_{t}$, $Y_{t}$, $x_{p}$)}
			\begin{algorithmic}[1]
			    \State neighbors = [\,]
			    \Comment Initialize min-heap
			    \For{each row ($x$,$y$) in ($X_{t}$, $Y_{t}$)}
			    \Comment Find $k$ nearest neighbors
			        \State distance\textunderscore tuple = ($-d(x, x_{p}), x, y$)
			        \If{$|\text{neighbors}|<k$}
			            \State push(neighbors, distance\textunderscore tuple)
			        \Else
			            \State pushpop(neighbors, distance\textunderscore tuple)
			        \EndIf
			    \EndFor
			    \If{weight='uniform'}
			    \Comment Prediction
			        \State prediction $= \frac{1}{k}\sum_{i=1}^k$ neighbors$[i][2]$
			    \ElsIf{weight='distance'}
			        \State prediction $= \frac{\sum_{i=1}^k neighbors[i][0] \cdot neighbors[i][2]}{\sum_{i=1}^k neighbors[i][0]}$
			    \EndIf
			    \State \Return prediction
			\end{algorithmic}
		\end{algorithm}
    \end{frame}

    \begin{frame}[fragile]{Results}
        \begin{itemize}
            \item Distance function:
                \begin{enumerate}
                    \item For Diamonds and Life Expectancy data set: Manhattan distance best results, but Euclidean distance also pretty good
                    \item For Concrete data set: Euclidean distance best, but Manhattan also good
                    \item Chebyshev distance generally not optimal for our data sets
                \end{enumerate}
            \item $k$ value:
                \begin{enumerate}
                    \item Not the same optimal $k$ value for all our data sets
                \end{enumerate}

            \item Scaling:
                \begin{enumerate}
                    \item Best results for all data sets obtained with standard-Scaling
                    \item Min-Max-Scaler resp. without scaling not really good
                \end{enumerate}
        \end{itemize}
    \end{frame}

    \begin{frame}{Performance on Diamonds Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_knn_scores_mean_sq_err.png}
            \caption{Mean squared error of $k$-NN on Diamonds Data Set}
            \label{fig:kNN_Diamond_MSE}
       \end{figure}
    \end{frame}

    \begin{frame}{Performance on Diamonds Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_knn_scores_max_error.png}
            \caption{Max. error of $k$-NN on Diamonds Data Set}
            \label{fig:kNN_Diamond_max-error}
       \end{figure}
    \end{frame}

    \begin{frame}{Performance on Concrete Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_knn_scores_mean_sq_err.png}
            \caption{Mean squared error of $k$-NN on Concrete Data Set}
            \label{fig:kNN_concrete_MSE}
       \end{figure}
    \end{frame}

    \begin{frame}{Performance on Concrete Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_knn_scores_max_error.png}
            \caption{Max. error of $k$-NN on Concrete Data Set}
            \label{fig:kNN_concrete_max-error}
       \end{figure}
    \end{frame}

    \begin{frame}{Performance on Life Expectancy Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_knn_scores_mean_sq_err.png}
            \caption{MSE of k-NN on Life Expectancy Data Set}
            \label{fig:kNN_LE_MSE}
        \end{figure}    
    \end{frame}

    \begin{frame}{Performance on Life Expectancy Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_knn_scores_max_error.png}
            \caption{Max. error of k-NN on Life Expectancy Data Set}
            \label{fig:kNN_LE_max-error}
        \end{figure}    
    \end{frame}

    \begin{frame}{Performance on Diamonds Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_knn_scores_runtime.png}
            \caption{Prediction time of $k$-NN on Diamonds Data Set}
            \label{fig:kNN_Diamond_runtime}
       \end{figure}
    \end{frame}

    \begin{frame}{Runtime on Concrete Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_knn_scores_runtime.png}
            \caption{Prediction time of $k$-NN on Concrete Data Set}
            \label{fig:kNN_concrete_runtime}
       \end{figure}
    \end{frame}

    \begin{frame}{Runtime on Life Expectancy Data Set}
        \begin{figure}[h!]
            \centering
            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_knn_scores_runtime.png}
            \caption{Prediction time of $k$-NN on Life Expectancy Data Set}
            \label{fig:kNN_LE_runtime}
        \end{figure}    
    \end{frame}

\section[Comparison with other algorithms]{Comparison with other algorithms}
    \begin{frame}[fragile]{Comparison with other algorithms}
        \begin{tabular}{l|c|c|r|c|c|c}
             \multirow{2}{*}{}& \multicolumn{2}{c|}{Diamonds} & \multicolumn{2}{c|}{Concrete} & \multicolumn{2}{c}{Life Expectancy} \\
             & MSE & Max. err. & MSE & Max. err. & MSE & Max. err. \\
                \hline
            $k$-NN & $4.4 \cdot 10^6$ & $9.5 \cdot 10^3$ & 65 & 27 & 16 & 15 \\
                \hline
            GD & $9.9 \cdot 10^6$ & $7.5 \cdot 10^3$ & 109 & 31 & 21 & 20 \\
                \hline
            DT & $3.9\cdot 10^6$ & $8.0 \cdot 10^3$ & 42 & 31 & 14 & 15 \\
                \hline
            RF & $3.5 \cdot 10^6$ & $6.5 \cdot 10^3$ & 25 & 23 & 8 & 12 \\
        \end{tabular}

        $k$-NN...implemented $k$-NN \\
        GD...implemented Gradient Descent \\
        DT...Decision tree of sklearn (with default parameters) \\
        RF... Random forest of sklearn (with default parameters)
    \end{frame}

\section[Conclusion]{Conclusion}
    \begin{frame}[fragile]{Conclusion Gradient Descent}
        \begin{itemize}
            \item Our implementation was worse than the sklearn implementation regarding the performance metrics, but behaved similar

            \item Additionally, the runtime of our implementation was higher compared to the sklearn version

            \item To achieve similar results as in sklearn, a higher number of iterations was needed

            \item Our algorithm worked the best for $\alpha=10^{-2}$ in our tests, across all data sets

            \item Standard-Scaling improved the results
        \end{itemize}
    \end{frame}

    \begin{frame}[fragile]{Conclusion $k$-NN}
        \begin{itemize}
            \item Our $k$-NN implementation achieved the same results as in sklearn, also with an similar runtime

            \item Different optimal $k$ values for different data sets

            \item Manhattan distance performed best resp. always really good

            \item Using the inverse distance as weights yielded better scores than uniform weights

            \item Standard-Scaling improved the results
        \end{itemize}
    \end{frame}

\begin{frame}[allowframebreaks]{References}
    \bibliography{demo}
    \bibliographystyle{abbrv}

    \bibitem{diamonds}
        Diamonds Data Set: \url{www.openml.org/d/42225}

    \bibitem{concrete}
        Concrete Data Set: \url{www.kaggle.com/prokaggler/concrete-data}

    \bibitem{life-expectancy}
        Life Expectancy Data Set: \url{www.kaggle.com/kumarajarshi/life-expectancy-who}
\end{frame}
\end{document}

### 2021-02-20 exercise_3/paper/paper_ex3.tex
Add files via upload

\documentclass[a4paper,11pt]{article}
\usepackage[a4paper,left=3.1cm,right=3.1cm,top=3cm,bottom=2.9cm]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amssymb,amsfonts,stmaryrd, wasysym}
\usepackage{color}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{multirow} %multirow in table

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{titling}
\usepackage{caption}
\usepackage{hyperref}
\captionsetup{font=footnotesize}

\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

%%%%%%%%%%%%%%%%% Kopf- & Fußzeile %%%%%%%%%%%%%%%%%
\usepackage[footsepline]{scrlayer-scrpage}
\pagestyle{scrheadings}
\clearscrheadfoot
\title{Machine Learning - Exercise 3}
\subtitle{Model Stealing/Extraction}
\author{Christian Hatschka, Daniel Fangl, Esra Ceylan}
\date{February 2021}
\ihead{\thetitle}
\ifoot{\newline \theauthor}
\ofoot{\newline \pagemark}
\setlength{\headheight}{15pt}
\setlength{\footheight}{29pt}

\begin{document}
\maketitle

\section{Group members}
    Daniel Fangl (01526097) has a bachelor in Software Engineering and is currently in the master course Software Engineering and Internet Computing. Christian Hatschka (01525634) and Esra Ceylan (01526801) both have a bachelor in Mathematics and are currently enrolled in the master course Logic and Computation.

\section{Introduction}
    As the construction of a good model is an expensive and time consuming task, the thought of training a model based on an existing but not explicitly given one is interesting. We will do this using the original model as a black-box and taking its predictions into account.

    The aim of this project is to extract several models by using different model-stealing methods. Moreover, we will test their efficiency and accuracy and compare their performance to the performance of the underlying original model.

\section{Copycat Networks for CNN}
    This model stealing attack was proposed by Correia-Silva et al.~\cite{copycat} and aims to copy a Convolutional Neural Network. First, we will use the target CNN as a black-box to label our training set, which can also contain instances from the non-problem domain if the model allows us to classify them. For example the Microsoft Azure Emotion API does not allow to upload instances, where it cannot detect a face, hence which are not part of the problem-domain. Even images containing a face can sometimes be rejected as the API could not always detect a face. By classifying the data we create a fake dataset which will be used to train the extracted model.

    Next, we select a model architecture of the copycat network. A possible problem with this approach is that we might not know the model architecture of the original network. However, this should not be a big problem as the knowledge can be copied to a different model.
    As pre-trained models tend to perform better, we used the VGG-16 architecture with pre-trained weights. It is obviously optimal if the pre-trained model is already close to the problem domain. In the next step we use the generated dataset to fit the pre-trained model.

    As described in~\cite{copycat} we will use Stochastic Gradient Descent with a Step Down policy for the learning rate for training the copycat model.

    \subsection{First Data set}
        As our first data set we combined the data sets described in the following two subsections. 
        %Since KDEF and AKDEF were one of the used data sets in the paper of Correia-Silva et al. we wanted to take them as validation that we achieve similar results. Unfortunately, they contain only about 5\,000 samples in total and we could not get access to other data sets used in the paper. Therefore, we combined them with a larger data set.
        Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results to the results in the paper. Therefore, we used different data sets and combined them to obtain a larger number of instances.

        \subsubsection{KDEF and AKDEF}
            The Karolinska directed emotional faces data set~\cite{kdef} (short KDEF) contains 4\,900 images of human facial expressions. The pictures were taken of 70 different people (35 male and 35 female) displaying 7 different emotional expressions. All people portrayed were amateur actors between the ages of 20 and 30 and had no facial hair, glasses or makeup during the photos. Each of the expressions were taken from multiple different angles.

            The averaged Karolinska directed emotional faces data set~\cite{kdef} (short AKDEF) contains $70$ averaged images of KDEF. The averaging was done over images containing the same gender, angle and emotional expression.

            Both data sets contain labels and were made by the Karolinska Institute in Stockholm, Sweden by the Department of Clinical Neuroscience in 1998. The data sets have been used in a large number of research publications on the topic.

        \subsubsection{Emotion Detection from Facial Expressions}
            This data set was taken from the Kaggle competition 'Emotion Detection From Facial Expressions'~\cite{kaggle-emotion}. 
            It contains 13\,690 images of human faces with different emotions. The data set was constructed from a variety of different sources, e.g.
            \begin{itemize}
                \item labeled Faces In The Wild,
                \item the Japanese Female Facial Expression (JAFFE) Database,
                \item indian Movie Face database (IMFDB),
                \item the Extended Yale Face Database B.
            \end{itemize}

            Additionally, this data set contains labeled data, like the previous set, allowing us also to compare the overall performance of the original model and the extracted one.

    \subsection{Microsoft Azure Emotion API}
        As our first target model we chose the publicly available Microsoft Azure Emotion API. For an input image it returns a confidence across a set of emotions for each face in the image.

        This API classifies the emotion a face portrays, in the form of a percentage vectors that assigns values to the following emotions:
            \begin{itemize}
                \item Anger
                \item Contempt
                \item Disgust
                \item Fear
                \item Happiness
                \item Neutral
                \item Sadness
                \item Surprise
            \end{itemize}
        For example the following face from the publicly available Karolinska Directed Emotional Faces (KDEF) dataset, returned a vector that assigned a percentage of $0.999$ to Happiness $0.001$ to Surprise and $0$ to everything else.
            \begin{figure}[h!]
                    \centering      \includegraphics[scale=0.2]{exercise_3/paper/images/AM18HAS.JPG}
                    \caption{A face classified as happy by Azure}
                    \label{fig:Happy_face}
            \end{figure}

        There is a free pricing option as well as a premium plan. As Microsoft has a promotion for students, which gives 100€ of free credit, we chose the premium plan which allows us to submit up to 10 images per second.

        We started by stealing the model behind this API as it was already copied in the paper and as such we could assess whether the performance of our copied classifier was similar to the performance of the stolen classifier in the paper.

        Originally the plan was to add images, which are not part of the problem domain to the images to be classified by the blackbox, however as Azure does not classify images in which it does not recognise any faces, this was not possible.

        Testing the Azure Classifier using the prelabeled data from the Kaggled Competion we got an accuracy of $0.76$.

    \subsection{Evaluation 1}
        We used the Karolinska Directed Emotional Faces (KDEF) and Averaged Karolinska Directed Emotional Faces (AKDEF) dataset to query Azure as a Blackbox. As Azure did not recognise some of the faces we added No face detected as an additional class. \\

        The Cnn-Classifier was trained through by a Multi-layer perceptron. As the Copying algorithm used for this Classifier was rather basic we mapped the size of the training set to the size of the subset of AKDEF/KDEF used to train our copy-cat.\\

        In order to compare the performance of our copied classifier to the original we used the ..\todo[]{dataset}.

        \todo[]{graph}

    \subsection{Second Data Set}
        https://www.kaggle.com/crawford/cat-dataset 9000 Bilder

        http://vision.stanford.edu/aditya86/ImageNetDogs/ 20 580 Bilder

\section{Classifier 2}

\section{Conclusions}

\bibliographystyle{abbrv}
\bibliography{literature}

\end{document}

### 2021-02-20 exercise_3/presentation/presentation_ex3.tex
Add files via upload

--- 2021-02-20 exercise_2/presentation/Presentation_P2.tex
@@
 
-\title{Machine Learning - Exercise 2}
-\subtitle{Regression}
+\title{Machine Learning - Exercise 3}
+\subtitle{Model Stealing/Extraction}
 % \date{\today}
@@
 \maketitle
-
 \begin{frame}{Table of contents}
@@
 \end{frame}
-
-\section[Data Sets]{Data Sets}
-    \begin{frame}[fragile]{Diamonds Data Set}
-        Several attributes of diamonds, e.g. carat, clarity or measurements has been collected.
-
+\section[Copy-Cat Stealing]{Copy-Cat Stealing}
+\begin{frame}[fragile]{Basics}
 \begin{itemize}
-            \item \#samples = $ 53\,940$
-            \item \#attributes = $9$
-            \item $6$ numeric and $3$ categorical attributes
-            \item No missing values
-            \item To predict: price in US Dollars
+    \item Uses model as blackbox
+    \item unlabeled images (domain + non-domain)
+    \item Stochastic Gradient Descent with a Step Down policy for learning rate
 \end{itemize}
 \end{frame}
+\subsection[Microsoft Azure API]{Microsoft Azure API}
 
-    \begin{frame}[fragile]{Concrete Data Set}
-        Data set contains information about the composition as well as the age of cement in days and it's compressive strength.
+\begin{frame}[fragile]{Azure API}
 \begin{itemize}
-            \item \#samples = $ 1\,030$
-            \item \#attributes = $8$
-            \item Only numeric attribute
-            \item Has no missing values
-            \item To predict: concrete compressive strength measured in MPa
+    \item Gives a percentage vector of emotions (Anger, Contempt, Disgust, Fear, Happiness, Neutral, Sadness, Surprise)
+    \item No such vector if it doesn't recognise a face$\Rightarrow$Only domain data
+    \item Free to use but has premium plan
 \end{itemize}
 \end{frame}
+\begin{frame}[fragile]{The dataset}
+\noindent\begin{minipage}{\textwidth}% adapt widths of minipages to your needs
+\begin{itemize}
+\item KDEF and AKDEF 
+\item Emotion Detection from Facial Expressions
+\item contains already labeled data
+\end{itemize}
+\end{minipage}
 
-    \begin{frame}[fragile]{Life Expectancy Data Set}
-        Data set contains health factors of 193 countries between the years $2000$ to $2015$.
-
-        \begin{itemize}
-            \item \#samples = $ 2\,938$
-            \item \#attributes = $20$
-            \item $19$ numeric attributes and $1$ categorical feature
-            \item Has missing values
-            \item To predict: life expectancy in years
-        \end{itemize}
-    \end{frame}
-
-\section[Data Preparation]{Data Preparation}
-    \begin{frame}[fragile]{Data Preparation}
-        \begin{enumerate}
-            \item Categorical data:
-                \begin{itemize}
-                    \item One-hot encoding
-                \end{itemize}
-
-            \item Missing values:
-                \begin{itemize}
-                    \item Most common value
-                    \item Median
-                \end{itemize}
-
-            \item Scaling:
-                \begin{itemize}
-                    \item Without
-                    \item Standard-Scaler 
-                    \item Min-Max-Scaler
-                \end{itemize}
-        \end{enumerate}
-    \end{frame}
-
-\section[Gradient Descent]{Gradient Descent Algorithm}
-    \begin{frame}[fragile]{Gradient Descent}
-        \begin{itemize}
-            \item $n=\#attributes$
-            \item Weight vector $\w = (w_0, ..., w_n)'$
-            \item Minimize error by computing impact of all $w_j$:
-                \begin{align*}
-                    \min MSE(\w) &= \min \frac{1}{\#samples} RSS(\w) \\
-                    &= \min \frac{1}{\#samples} \sum_{i=1}^{\#samples}(y_i - (w_0 + \sum_{j=1}^{n}w_{j} x_{ij}))^2
-                \end{align*}
-                Use $MSE$ instead of $RSS$ as cost function because even for different values for $\alpha$ the weights do not converge for data set with big sample size
-        \end{itemize}
-    \end{frame}
-
-    \begin{frame}[fragile]{Gradient Descent: Pseudocode}
-        \begin{algorithm}[H]
-            \caption{GD-Regressor($\alpha$, $max\textunderscore iterations$, $X_{t}$, $Y_{t}$)}
-			\begin{algorithmic}[1]
-			    \For{$j=0$ to $n$} 
-			    \Comment Initialize weights
-			        \State $w_j=1$ 
-			    \EndFor
-				\For{$k = 1$ to $max\textunderscore iterations$}
-    				\For{$j=0$ to $n$}
-    				\Comment Calculate derivative
-    				    \State Calculate $\costder$
-    				\EndFor
-    				\For{$j=0$ to $n$}
-    				\Comment Update weights
-    				    \State $w_j = w_j - \alpha \costder$
-    				\EndFor
-				\EndFor
-				\State \Return $\w$
-			\end{algorithmic}
-		\end{algorithm}
-    \end{frame}
-
-    \begin{frame}[fragile]{Calculating Partial Derivative}
-        \begin{enumerate}
-            \item Manually calculated:
-                \begin{align*}
-                    \costder = \left\{
-                    	\begin{array}{ll}
-                    		\frac{-2}{\#samples} \sum_{i=1}^{\#samples}(y_i - (w_0 + \sum_{j=1}^{n}w_{j} x_{ij})), & j=0, \\
-                    		\frac{-2}{\#samples} \sum_{i=1}^{\#samples}(y_i - (w_0 + \sum_{j=1}^{n}w_{j} x_{ij}))\cdot x_{ik},  & j \geq 1.
-                    	\end{array}
-                    \right.
-                \end{align*}
-                $\rightarrow$ too slow because of huge number of arithmetic operations $\sim 2n \cdot \#samples$.
-
-            \item In terms of vector-operations:
-
-                $\Tilde{X_t} \in \R^{\#samples \times (n+1)}$...insert first column with $1$ to training set $X_t$
-
-                \begin{align*}
-                    \left( \costder \right)_{j=0,...,n} = \frac{-2}{\#samples} \Tilde{X_t}' \cdot \left(Y_t - \Tilde{X_t} \cdot \w \right) 
-                \end{align*}
-                $\rightarrow$ much faster
-        \end{enumerate}
-    \end{frame}
-
-    \begin{frame}[fragile]{Gradient Descent: Pseudocode Prediction}
-        \begin{algorithm}[H]
-            \caption{GD-Prediction($\w$, $X_p$)}
-			\begin{algorithmic}[1]
-			    \State $\Tilde{X_p}$ := insert first column with $1$ to $X_p$
-			    \State $Y = \Tilde{X_p} \cdot \w$
-			    \State \Return $Y$
-			\end{algorithmic}
-		\end{algorithm}
-		Again, using vector operations made the prediction much faster.
-    \end{frame}
-
-    \begin{frame}{Results}
-        \begin{itemize}
-            \item Vector operations way faster than simply summing up
-            \item Although very fast takes more iterations to reach similar results as in sklearn
-            \item Weight initialization has an impact on iterations needed till convergence $\rightarrow$ done differently in sklearn
-
-            \item For all our data sets best results using Standard-Scaling
-            \item Min-Max-Scaler was not bad, but also not really good
-            \item Without scaling weights get too big $\rightarrow$ do not converge
-
-            \item In the following plots we used $\alpha=10^{-2}$ for our implementation of Gradient Descent (best $\alpha$ in our tests) and $\alpha=10^{-5}$ for the scikitlearn implementation
-        \end{itemize}
-    \end{frame}
-
-    \begin{frame}{Performance on Diamonds Data Set}
  \begin{figure}[h!]
         \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_scores_mean_sq_err.png}
-            \caption{Mean squared error of Gradient Descent on Diamonds Data Set}
-            \label{fig:Grad_Diamond_MSE}
+        \begin{subfigure}[c]{0.45\textwidth}
+            \centering
+            \includegraphics[width=0.9\textwidth]{exercise_3/paper/images/AM18HAS.JPG}
+            \caption{A face from KDEF}
+            \label{fig:KDEF_face}
+        \end{subfigure}
+        \begin{subfigure}[c]{0.45\textwidth}
+            \centering
+            \includegraphics[width=1\textwidth]{exercise_3/paper/images/FANHL.JPG}
+            \caption{A face from AKDEF}
+            \label{fig:AKDEF_face}
+        \end{subfigure}
+        \caption{}
+        \label{fig:faces}
     \end{figure}
 \end{frame}
-
-    \begin{frame}{Performance on Diamonds Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_scores_max_error.png}
-            \caption{Max. error of Gradient Descent on Diamonds Data Set}
-            \label{fig:Grad_Diamond_max-error}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Performance on Concrete Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_gradient-descent_scores_mean_sq_err.png}
-            \caption{Mean squared error of Gradient Descent on Concrete Set}
-            \label{fig:Grad_Concrete_MSE}
-       \end{figure}    
-    \end{frame}
-
-    \begin{frame}{Performance on Concrete Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_gradient-descent_scores_max_error.png}
-            \caption{Max. error of Gradient Descent on Concrete Set}
-            \label{fig:Grad_Concrete_max-error}
-        \end{figure}        
-    \end{frame}
-
-    \begin{frame}{Performance on Life Expectancy Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_gradient-descent_scores_mean_sq_err.png}
-            \caption{MSE of Gradient Descent on Life Expectancy Data Set}
-            \label{fig:Grad_LE_MSE}
-       \end{figure}    
-    \end{frame}
-
-    \begin{frame}{Performance on Life Expectancy Data Set}
-          \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_gradient-descent_scores_max_error.png}
-            \caption{Max. error of Gradient Descent on Life Expectancy Data Set}
-            \label{fig:Grad_LE_max-error}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Runtime on Diamonds Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_scores_runtime.png}
-            \caption{Runtime of Gradient Descent on Diamonds Data Set}
-            \label{fig:Grad_Diamond_runtime}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Runtime on Concrete Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_gradient-descent_scores_runtime.png}
-            \caption{Runtime of Gradient Descent on Concrete Data Set}
-            \label{fig:Grad_Concrete_runtime}
-       \end{figure}        
-    \end{frame}
-
-    \begin{frame}{Runtime on Life Expectancy Data Set}
-          \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_gradient-descent_scores_runtime.png}
-            \caption{Runtime of Gradient Descent on Life expectancy Data Set}
-            \label{fig:Grad_LE_runtime}
-       \end{figure}
-    \end{frame}
-
-\section[$k$-NN]{$k$-NN Algorithm}
-    \begin{frame}[fragile]{$k$-NN}
-        $n$ = \#attributes
-
-        Distance functions (using numpy.linalg.norm in Python):
-            \begin{enumerate}
-                \item Manhattan distance: $d_1(x_1, x_2) = \sum_{i=1}^n |x_{1i} - x_{2i}|$
-                \item Euclidean distance: $d_2(x_1, x_2) = \sqrt{\sum_{i=1}^n (x_{1i} - x_{2i})^2}$
-                \item Chebyshev distance: $d_\infty(x_1, x_2) = \max_{i \in \{1,...,n\}}|x_{1i} - x_{2i}|$
-            \end{enumerate}
-
-        Weight:
-            \begin{enumerate}
-                \item Uniform $\rightarrow$ mean of predicted class of $k$ nearest neighbours
-                \item Distance based: $\frac{1}{d(x_1, x_2)+\varepsilon}$ (very small $\varepsilon>0$ to prevent division by $0$) $\rightarrow$ weighted mean of predicted class of $k$ nearest neighbours
-            \end{enumerate}
-    \end{frame}
-
-    \begin{frame}[fragile]{$k$-NN: Pseudocode}
-        \begin{algorithm}[H]
-            \caption{$k$-NN-Regressor($k$, distance-fct $d$, weight, $X_{t}$, $Y_{t}$, $x_{p}$)}
-			\begin{algorithmic}[1]
-			    \State neighbors = [\,]
-			    \Comment Initialize min-heap
-			    \For{each row ($x$,$y$) in ($X_{t}$, $Y_{t}$)}
-			    \Comment Find $k$ nearest neighbors
-			        \State distance\textunderscore tuple = ($-d(x, x_{p}), x, y$)
-			        \If{$|\text{neighbors}|<k$}
-			            \State push(neighbors, distance\textunderscore tuple)
-			        \Else
-			            \State pushpop(neighbors, distance\textunderscore tuple)
-			        \EndIf
-			    \EndFor
-			    \If{weight='uniform'}
-			    \Comment Prediction
-			        \State prediction $= \frac{1}{k}\sum_{i=1}^k$ neighbors$[i][2]$
-			    \ElsIf{weight='distance'}
-			        \State prediction $= \frac{\sum_{i=1}^k neighbors[i][0] \cdot neighbors[i][2]}{\sum_{i=1}^k neighbors[i][0]}$
-			    \EndIf
-			    \State \Return prediction
-			\end{algorithmic}
-		\end{algorithm}
-    \end{frame}
-
-    \begin{frame}[fragile]{Results}
-        \begin{itemize}
-            \item Distance function:
-                \begin{enumerate}
-                    \item For Diamonds and Life Expectancy data set: Manhattan distance best results, but Euclidean distance also pretty good
-                    \item For Concrete data set: Euclidean distance best, but Manhattan also good
-                    \item Chebyshev distance generally not optimal for our data sets
-                \end{enumerate}
-            \item $k$ value:
-                \begin{enumerate}
-                    \item Not the same optimal $k$ value for all our data sets
-                \end{enumerate}
-
-            \item Scaling:
-                \begin{enumerate}
-                    \item Best results for all data sets obtained with standard-Scaling
-                    \item Min-Max-Scaler resp. without scaling not really good
-                \end{enumerate}
-        \end{itemize}
-    \end{frame}
-
-    \begin{frame}{Performance on Diamonds Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_knn_scores_mean_sq_err.png}
-            \caption{Mean squared error of $k$-NN on Diamonds Data Set}
-            \label{fig:kNN_Diamond_MSE}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Performance on Diamonds Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_knn_scores_max_error.png}
-            \caption{Max. error of $k$-NN on Diamonds Data Set}
-            \label{fig:kNN_Diamond_max-error}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Performance on Concrete Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_knn_scores_mean_sq_err.png}
-            \caption{Mean squared error of $k$-NN on Concrete Data Set}
-            \label{fig:kNN_concrete_MSE}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Performance on Concrete Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_knn_scores_max_error.png}
-            \caption{Max. error of $k$-NN on Concrete Data Set}
-            \label{fig:kNN_concrete_max-error}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Performance on Life Expectancy Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_knn_scores_mean_sq_err.png}
-            \caption{MSE of k-NN on Life Expectancy Data Set}
-            \label{fig:kNN_LE_MSE}
-        \end{figure}    
-    \end{frame}
-
-    \begin{frame}{Performance on Life Expectancy Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_knn_scores_max_error.png}
-            \caption{Max. error of k-NN on Life Expectancy Data Set}
-            \label{fig:kNN_LE_max-error}
-        \end{figure}    
-    \end{frame}
-
-    \begin{frame}{Performance on Diamonds Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/diamond_knn_scores_runtime.png}
-            \caption{Prediction time of $k$-NN on Diamonds Data Set}
-            \label{fig:kNN_Diamond_runtime}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Runtime on Concrete Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/concrete_knn_scores_runtime.png}
-            \caption{Prediction time of $k$-NN on Concrete Data Set}
-            \label{fig:kNN_concrete_runtime}
-       \end{figure}
-    \end{frame}
-
-    \begin{frame}{Runtime on Life Expectancy Data Set}
-        \begin{figure}[h!]
-            \centering
-            \includegraphics[width=0.8\textwidth]{exercise_2/presentation/figures/le_knn_scores_runtime.png}
-            \caption{Prediction time of $k$-NN on Life Expectancy Data Set}
-            \label{fig:kNN_LE_runtime}
-        \end{figure}    
-    \end{frame}
-
-\section[Comparison with other algorithms]{Comparison with other algorithms}
-    \begin{frame}[fragile]{Comparison with other algorithms}
-        \begin{tabular}{l|c|c|r|c|c|c}
-             \multirow{2}{*}{}& \multicolumn{2}{c|}{Diamonds} & \multicolumn{2}{c|}{Concrete} & \multicolumn{2}{c}{Life Expectancy} \\
-             & MSE & Max. err. & MSE & Max. err. & MSE & Max. err. \\
-                \hline
-            $k$-NN & $4.4 \cdot 10^6$ & $9.5 \cdot 10^3$ & 65 & 27 & 16 & 15 \\
-                \hline
-            GD & $9.9 \cdot 10^6$ & $7.5 \cdot 10^3$ & 109 & 31 & 21 & 20 \\
-                \hline
-            DT & $3.9\cdot 10^6$ & $8.0 \cdot 10^3$ & 42 & 31 & 14 & 15 \\
-                \hline
-            RF & $3.5 \cdot 10^6$ & $6.5 \cdot 10^3$ & 25 & 23 & 8 & 12 \\
-        \end{tabular}
-
-        $k$-NN...implemented $k$-NN \\
-        GD...implemented Gradient Descent \\
-        DT...Decision tree of sklearn (with default parameters) \\
-        RF... Random forest of sklearn (with default parameters)
-    \end{frame}
-
-\section[Conclusion]{Conclusion}
-    \begin{frame}[fragile]{Conclusion Gradient Descent}
-        \begin{itemize}
-            \item Our implementation was worse than the sklearn implementation regarding the performance metrics, but behaved similar
-
-            \item Additionally, the runtime of our implementation was higher compared to the sklearn version
-
-            \item To achieve similar results as in sklearn, a higher number of iterations was needed
-
-            \item Our algorithm worked the best for $\alpha=10^{-2}$ in our tests, across all data sets
-
-            \item Standard-Scaling improved the results
-        \end{itemize}
-    \end{frame}
-
-    \begin{frame}[fragile]{Conclusion $k$-NN}
-        \begin{itemize}
-            \item Our $k$-NN implementation achieved the same results as in sklearn, also with an similar runtime
-
-            \item Different optimal $k$ values for different data sets
-
-            \item Manhattan distance performed best resp. always really good
-
-            \item Using the inverse distance as weights yielded better scores than uniform weights
-
-            \item Standard-Scaling improved the results
-        \end{itemize}
-    \end{frame}
-
-\begin{frame}[allowframebreaks]{References}
-    \bibliography{demo}
-    \bibliographystyle{abbrv}
-
-    \bibitem{diamonds}
-        Diamonds Data Set: \url{www.openml.org/d/42225}
-
-    \bibitem{concrete}
-        Concrete Data Set: \url{www.kaggle.com/prokaggler/concrete-data}
-
-    \bibitem{life-expectancy}
-        Life Expectancy Data Set: \url{www.kaggle.com/kumarajarshi/life-expectancy-who}
-\end{frame}
 \end{document}

### 2021-02-20 exercise_3/paper/paper_ex3.tex
Updates from Overleaf

@@
 
-    Next, we select a model architecture of the copycat network.
+    Next, we will select a model architecture of the copycat network.
 A possible problem with this approach is that we might not know the model architecture of the original network.
 However, this should not be a big problem as the knowledge can be copied to a different model.
-    As pre-trained models tend to perform better, we used the VGG-16 architecture with pre-trained weights.
-It is obviously optimal if the pre-trained model is already close to the problem domain.
-In the next step we use the generated dataset to fit the pre-trained model.
+    As pre-trained models tend to perform better, we will use the VGG-16 architecture with pre-trained weights. It is obviously optimal if the pre-trained model is already close to the problem domain.
 
+    In the next step we will use the generated data set to fit the pre-trained model.
     As described in~\cite{copycat} we will use Stochastic Gradient Descent with a Step Down policy for the learning rate for training the copycat model.
@@
     \subsection{First Data set}
-        As our first data set we combined the data sets described in the following two subsections. 
+        Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results to the results in the paper.
+Therefore, we used other data sets for our experiments.
+We combined two sets, which are described in the following two subsections, to obtain a larger number of instances.
+        %As our first data set we combined the data sets described in the following two subsections. 
         %Since KDEF and AKDEF were one of the used data sets in the paper of Correia-Silva et al.
@@
 Therefore, we combined them with a larger data set.
-        Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results to the results in the paper.
-Therefore, we used different data sets and combined them to obtain a larger number of instances.
 
@@
     \subsection{Microsoft Azure Emotion API}
-        As our first target model we chose the publicly available Microsoft Azure Emotion API. For an input image it returns a confidence across a set of emotions for each face in the image.
-
-        This API classifies the emotion a face portrays, in the form of a percentage vectors that assigns values to the following emotions:
+        As our first target model we used the publicly available Microsoft Azure Emotion API.
+For an input image this API returns a percentage vector of emotions for each face in the image.
+For each of the following emotions a value is assigned:
+        %This API classifies the emotion a face portrays, in the form of a percentage vectors that assigns values to the following emotions:
             \begin{itemize}
@@
             \end{itemize}
-        For example the following face from the publicly available Karolinska Directed Emotional Faces (KDEF) dataset, returned a vector that assigned a percentage of $0.999$ to Happiness $0.001$ to Surprise and $0$ to everything else.
+        For example the face in Figure~\ref{fig:happy_face} from the publicly available KDEF dataset returned a vector that assigned a percentage of $0.999$ to happiness $0.001$ to surprise and $0$ to everything else.
             \begin{figure}[h!]
                     \centering      \includegraphics[scale=0.2]{exercise_3/paper/images/AM18HAS.JPG}
-                    \caption{A face classified as happy by Azure}
-                    \label{fig:Happy_face}
+                    \caption{Face classified as happy by Azure}
+                    \label{fig:happy_face}
             \end{figure}
 
-        There is a free pricing option as well as a premium plan.
-As Microsoft has a promotion for students, which gives 100€ of free credit, we chose the premium plan which allows us to submit up to 10 images per second.
+        In the Microsoft Azure Emotion API there is a free pricing option which allows us to submit up to 20 images per minute as well as a premium plan with up to 10 calls per second.
+As Microsoft has a promotion for students, which gives 100€ of free credit, we chose the premium plan.
+%which allows us to submit up to 10 images per second.
 
-        We started by stealing the model behind this API as it was already copied in the paper and as such we could assess whether the performance of our copied classifier was similar to the performance of the stolen classifier in the paper.
+        We started with stealing the model behind this API as it was already considered in the paper.
+Hence, we can assess whether the performance of our copied classifier is similar to the performance of the stolen classifier in the paper.
 
-        Originally the plan was to add images, which are not part of the problem domain to the images to be classified by the blackbox, however as Azure does not classify images in which it does not recognise any faces, this was not possible.
+        Originally, we wanted to add instances, which are not part of the problem domain to our fake dataset.
+However, as Azure does not classify images in which it does not detect any face, this was not possible.
 
-        Testing the Azure Classifier using the prelabeled data from the Kaggled Competion we got an accuracy of $0.76$.
+        Testing the Azure Classifier using the pre-labeled data from the Kaggle Competion we got an accuracy of $0.76$. \todo{in Evaluation}
 
@@
 As Azure did not recognise some of the faces we added No face detected as an additional class.
-\\
+\todo{no face detected in 3.2}
 
-        The Cnn-Classifier was trained through by a Multi-layer perceptron.
-As the Copying algorithm used for this Classifier was rather basic we mapped the size of the training set to the size of the subset of AKDEF/KDEF used to train our copy-cat.\\
+        The CNN-Classifier was trained through by a Multi-layer perceptron.
+As the Copying algorithm used for this Classifier was rather basic we mapped the size of the training set to the size of the subset of AKDEF/KDEF used to train our copy-cat.
 
-        In order to compare the performance of our copied classifier to the original we used the ..\todo[]{dataset}.
-
-        \todo[]{graph}
+        In order to compare the performance of our copied classifier to the original we split the data set into a test and training set and looked at the accuracy resp.
+equality of our copied model, dependant on the size of the set used to train the model.
+We trained the model on progressively larger subsets of the training set, which were included in each other.
 
     \subsection{Second Data Set}
+        Model: https://www.kaggle.com/c/dogs-vs-cats/data
+
+        Attack and Test:
+
         https://www.kaggle.com/crawford/cat-dataset 9000 Bilder

### 2021-02-20 exercise_3/paper/paper_ex3.tex

@@
 
-\section{Copycat Networks for CNN}
+\section{Copycat Networks for CNN}\label{sec:copycat}
     This model stealing attack was proposed by Correia-Silva et al.~\cite{copycat} and aims to copy a Convolutional Neural Network.
@@
 
-    \subsection{First Data set}
+    \subsection{First Data Set}
         Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results to the results in the paper.
@@
             This data set was taken from the Kaggle competition 'Emotion Detection From Facial Expressions'~\cite{kaggle-emotion}. 
-            It contains 13\,690 images of human faces with different emotions. The data set was constructed from a variety of different sources, e.g.
+            It contains 13\,690 images of several human faces with different emotions. The data set was constructed from a variety of different sources, e.g.
             \begin{itemize}
@@
                 \item the Japanese Female Facial Expression (JAFFE) Database,
-                \item indian Movie Face database (IMFDB),
+                \item Indian Movie Face database (IMFDB),
                 \item the Extended Yale Face Database B.
@@
 
-            Additionally, this data set contains labeled data, like the previous set, allowing us also to compare the overall performance of the original model and the extracted one.
+            Additionally, this data set contains, like the previous one, labeled data allowing us to compare the performance of the extracted model and also the overall performance of the target network.
 
@@
 For an input image this API returns a percentage vector of emotions for each face in the image.
-For each of the following emotions a value is assigned:
+The following emotions are measured:
         %This API classifies the emotion a face portrays, in the form of a percentage vectors that assigns values to the following emotions:
@@
             \end{itemize}
-        For example the face in Figure~\ref{fig:happy_face} from the publicly available KDEF dataset returned a vector that assigned a percentage of $0.999$ to happiness $0.001$ to surprise and $0$ to everything else.
+        For example the face in Figure~\ref{fig:happy_face} from the publicly available KDEF data set returns a vector assigning a percentage of $0.999$ to happiness, $0.001$ to surprise and $0$ to everything else.
             \begin{figure}[h!]
                     \centering      \includegraphics[scale=0.2]{exercise_3/paper/images/AM18HAS.JPG}
-                    \caption{Face classified as happy by Azure}
+                    \caption{Face classified as happy by the Azure Emotion API}
                     \label{fig:happy_face}
@@
         In the Microsoft Azure Emotion API there is a free pricing option which allows us to submit up to 20 images per minute as well as a premium plan with up to 10 calls per second.
-As Microsoft has a promotion for students, which gives 100€ of free credit, we chose the premium plan.
+As Microsoft has a promotion for students, which gives 100€ free credit, we chose the premium plan.
 %which allows us to submit up to 10 images per second.
 
-        We started with stealing the model behind this API as it was already considered in the paper.
-Hence, we can assess whether the performance of our copied classifier is similar to the performance of the stolen classifier in the paper.
+        We decided to steal the model behind this API because this is also considered in the paper by Correia-Silva et al.~\cite{copycat}.
+Hence, we are able to assess whether the performance of our extracted classifier is similar to the performance of the extracted classifier in the paper.
 
-        Originally, we wanted to add instances, which are not part of the problem domain to our fake dataset.
+       As mentioned in the beginning of Section~\ref{sec:copycat} Azure could not recognise all of the faces in our data set and hence could not classify for each face an emotion.
+Therefore, we added to the 8 emotions a further class called 'no\textunderscore face'.
+
+        %Originally, we wanted to add instances, which are not part of the problem domain to our fake data set.
 However, as Azure does not classify images in which it does not detect any face, this was not possible.
 
-        Testing the Azure Classifier using the pre-labeled data from the Kaggle Competion we got an accuracy of $0.76$. \todo{in Evaluation}
+    \subsection{Evaluation 1}
+        Since we had labeled data, we were able to compute the accuracy of the Microsoft Azure Emotion API. On the whole data set we obtained an accuracy of $0.76$.
 
-    \subsection{Evaluation 1}
-        We used the Karolinska Directed Emotional Faces (KDEF) and Averaged Karolinska Directed Emotional Faces (AKDEF) dataset to query Azure as a Blackbox.
-As Azure did not recognise some of the faces we added No face detected as an additional class.
-\todo{no face detected in 3.2}
+        For testing the efficiency of our extracted model, we initially did a $75\%/25\%$ training/test split on our data set consisting of KDEF, AKDEF and the one from Kaggle.
+As we had labeled data, we had to delete the labels before querying the Azure API as a black-box.
+From now on we will refer to the training set as attack set, since this set will be used to attack the target network.
 
-        The CNN-Classifier was trained through by a Multi-layer perceptron.
-As the Copying algorithm used for this Classifier was rather basic we mapped the size of the training set to the size of the subset of AKDEF/KDEF used to train our copy-cat.
+        To learn the effect of the number if images in the training set, we used an incremental approach.
+We trained the model on progressively larger subsets of the training set, which were included in each other.
+Starting with a random sample $s_0$ of $2\,000$ images, the next training set $s_n$ consisted of $s_{n-1}$ and additional $1\,000$ images.
 
-        In order to compare the performance of our copied classifier to the original we split the data set into a test and training set and looked at the accuracy resp.
+        In order to compare the performance of our extracted models to the target network we considered two measures:
+        \begin{itemize}
+            \item Accuracy: correctly classified faces with respect to the original labels.
+            \item Equality: correctly classified faces with respect to the target network.  
+        \end{itemize}
+        %The CNN-classifier was trained by a Multi-layer Perceptron.
+As the copying algorithm used for this classifier was rather basic we mapped the size of the training set to the size of the subset of AKDEF/KDEF used to train our copy-cat.
+
+        %In order to compare the performance of our copied classifier to the original we split the data set into a test and training set and looked at the accuracy resp.
 equality of our copied model, dependant on the size of the set used to train the model.
@@
 
+        Figure~\ref{fig:performance-azure} shows the results of our tests.
+Overall it can be seen that the accuracy as well as the equality improve for larger training sets.
+The best value for the accuracy in our tests was $0.578$.
+which seems much better compared to the results from the paper with about $0.35$.
+We also computed the accuracy of the Azure Emotion API on the test set and obtained an accuracy of $0.764$.
+
+        However, the extracted model using the whole training set was was able to coincide on $70\%$ on the test data.
+
+        \begin{figure}[h!]
+            \centering
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/accuracy_copy_Azure.png}
+                \caption{Accuracy of the extracted models}
+                \label{fig:Accuracy_Azure}
+            \end{subfigure}
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/equality_copy_Azure.png}
+                \caption{Equality of the extracted models}
+                \label{fig:Equality_Azure}
+            \end{subfigure}
+            \caption{Performance of Copycat Attack on first data set}
+            \label{fig:performance-azure}
+        \end{figure}
+    The training of the biggest copied model took only roughly one hour, including the time needed to question the Azure API on the labeling of our data set.
+This was in part to the offer allowing students to get $100$\$ of credit for free and therefore letting us to label $10$ images per second.
+Had we used the free tier we would have needed roughly $16$ hours of time which is still a reasonable timeframe.
     \subsection{Second Data Set}
-        Model: https://www.kaggle.com/c/dogs-vs-cats/data
+        In the following problem, we want to predict if a certain image contains a cat, a dog or none of them.
 
-        Attack and Test:
+        For building a model we will again combine several data sets.
+First of all, we need a training set for training the target network.
+Additionally, we will need images for the attack resp.
+test set.
 
-        https://www.kaggle.com/crawford/cat-dataset 9000 Bilder
+        \subsubsection{Cat data set}
+            %https://www.kaggle.com/crawford/cat-dataset 9000 Bilder 
+            This data set taken from \hyperlink{https://archive.org/details/CAT_DATASET}{archive.org} contains roughly $10\,000$ images of cats in various positions.
+Additionally pointers to the eyes, ears and nose of the cats were given, however we did not use them in any capacity.
 
-        http://vision.stanford.edu/aditya86/ImageNetDogs/ 20 580 Bilder
+        \subsubsection{Stanford dogs data set }
+            The data set was built using images from ImageNet, by \hyperlink{http://vision.stanford.edu/aditya86/ImageNetDogs/}{Stanford university} , in order to help categorize images.
+It contains $20\,580$ pictures of dogs.
+It theoretically contains classifications for different breeds of dogs, but once again we did not use this.
 
-\section{Classifier 2}
+        \subsubsection{Common objects in context data set}
+            Since our model for this exercise was homemade, we could use copy-cat to it's full power and include non-domain data in our training set for our copy-cat model.
+For this we chose a dataset from \hyperlink{https://cocodataset.org/\#download}{Common objects in context} containing $118\,000$ images of trains.
+
+     \subsection{Dogs vs. Cats}
+            For the second attempt we chose to train our own CNN to steal to make matters more interesting.
+We trained our model using the following competition data set from \hyperlink{https://www.kaggle.com/c/dogs-vs-cats/data}{Kaggle}.
+\section{last classifier}
 

### 2021-02-20 exercise_3/presentation/presentation_ex3.tex
Updates from Overleaf

@@
             \centering
-            \includegraphics[width=1\textwidth]{exercise_3/paper/images/FANHL.JPG}
+            \includegraphics[width=0.9\textwidth]{exercise_3/paper/images/FANHL.JPG}
             \caption{A face from AKDEF}
@@
 \end{frame}
+\begin{frame}[fragile]{Evaluation}
+\begin{itemize}
+    \item Accuracy of Azure on labeled data roughly $0.76$
+    \item attack set: starting with $2000$ up to $13961$
+    \item Test set: $4654$
+\end{itemize}
+\end{frame}
+\begin{frame}[fragile]{Evaluation}
+           \begin{figure}[h!]
+                    \centering      \includegraphics[scale=0.8]{exercise_3/paper/images/accuracy_copy_Azure.png}
+                    \caption{Accuracy of the copied network}
+                    \label{fig:Ac_Azure}
+            \end{figure}
+
+\end{frame}
+\begin{frame}[fragile]{Evaluation}
+           \begin{figure}[h!]
+                    \centering      \includegraphics[scale=0.8]{exercise_3/paper/images/equality_copy_Azure.png}
+                    \caption{percentage of images labeled the same}
+                    \label{fig:Eq_AZure}
+            \end{figure}
+
+\end{frame}
 \end{document}

### 2021-02-20 exercise_3/paper/paper_ex3.tex

@@
 For example the Microsoft Azure Emotion API does not allow to upload instances, where it cannot detect a face, hence which are not part of the problem-domain.
-Even images containing a face can sometimes be rejected as the API could not always detect a face.
-By classifying the data we create a fake dataset which will be used to train the extracted model.
+Even images containing a face can sometimes be rejected as the Azure API could not always detect a face.
+By classifying the data using the target network as black-box we create a fake data set which will be used to train the extracted model.
 
@@
 
-    In the next step we will use the generated data set to fit the pre-trained model.
+    In the next step we will use the generated fake data set to fit the pre-trained model.
     As described in~\cite{copycat} we will use Stochastic Gradient Descent with a Step Down policy for the learning rate for training the copycat model.
@@
     \subsection{First Data Set}
-        Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results to the results in the paper.
+        Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results with the results in the paper.
 Therefore, we used other data sets for our experiments.
-We combined two sets, which are described in the following two subsections, to obtain a larger number of instances.
+We combined two sets, which are described in the following two subsections to obtain a larger number of instances.
         %As our first data set we combined the data sets described in the following two subsections. 
@@
         \end{figure}
-    The training of the biggest copied model took only roughly one hour, including the time needed to question the Azure API on the labeling of our data set.
+        The training of the biggest extracted model took only roughly one hour, including the time needed to question the Azure API on the labeling of our data set.
 This was in part to the offer allowing students to get $100$\$ of credit for free and therefore letting us to label $10$ images per second.
 Had we used the free tier we would have needed roughly $16$ hours of time which is still a reasonable timeframe.
+
     \subsection{Second Data Set}
@@
 We trained our model using the following competition data set from \hyperlink{https://www.kaggle.com/c/dogs-vs-cats/data}{Kaggle}.
+We trained it using the training set containing $25\,000$ images of cats and dogs.
+
+            We tested the accuracy of the set by mixing the cat data set and the Stanford dog data set and picking $7\,644$ random images out of it. The resulting accuracy was $0\,821$.
+    \subsection{Evaluation 2}
+    We extracted the model in two different ways.
+In one instance we used only images that are part of the domain, therefore pictures of cats and dogs, in the attack set.
+In the other instance we used a mixture of non-domain images and domain images in a $2$ to $5$ ratio, to let the original model confess its information.
+
+    We start by looking at the accuracy of the extracted model in both cases:
+            \begin{figure}[h!]
+            \centering
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/accuracy_copy_cat.png}
+                \caption{Accuracy using only problem domain}
+                \label{fig:Accuracy_Azure}
+            \end{subfigure}
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/equality_copy_cat_.png}
+                \caption{Accuracy using mixed instances }
+                \label{fig:Equality_Azure}
+            \end{subfigure}
+            \caption{Performance of Copycat Attack on first data set}
+            \label{fig:performance-azure}
+        \end{figure}
+
 \section{last classifier}
-
 \section{Conclusions}

### 2021-02-21 exercise_3/presentation/presentation_ex3.tex
Updates from Overleaf

@@
     \item Test set: $4654$
+    \item one hour including queries
 \end{itemize}
@@
 \end{frame}
+\subsection[Cats and dogs]{Cats and dogs}
+\begin{frame}[fragile]{Cats and dogs Model}
+\begin{itemize}
+\item CNN home trained on $25\,000$ images
+\item Accuracy: $0,821$
+\end{itemize}
+\end{frame}
+\begin{frame}[fragile]{Evaluation}
+                \begin{figure}[h!]
+            \centering
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat_domain.png}
+                \caption{Accuracy using only problem domain}
+                \label{fig:Accuracy_Cat_domain}
+            \end{subfigure}
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat.png}
+                \caption{Accuracy using mixed instances }
+                \label{fig:Accuracy_cat_mix}
+            \end{subfigure}
+            \caption{Accuracy of Copycat Attack on second data set}
+            \label{fig:accuracy_cat}
+        \end{figure}
+\end{frame}
+\begin{frame}[fragile]{Evaluation}
+       \begin{figure}[h!]
+            \centering
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat_domain.png}
+                \caption{Equality using only problem domain}
+                \label{fig:Equality_cat_domain}
+            \end{subfigure}
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat.png}
+                \caption{Equality using mixed instances}
+                \label{fig:Equality_cat_mix}
+            \end{subfigure}
+            \caption{Equality of Copycat Attack on second data set}
+            \label{fig:equality_cat}
+        \end{figure}
+\end{frame}
+\begin{frame}[fragile]{runtime}
+    \begin{figure}[h!]
+        \centering      \includegraphics[scale=0.4]{exercise_3/paper/images/Time_copy_cat.png}
+        \caption{Time needed to extract a model}
+        \label{fig:time_cat}
+    \end{figure}
+\end{frame}
+
 \end{document}

### 2021-02-21 exercise_3/paper/paper_ex3.tex

@@
 
-    \subsection{First Data Set}
+    We carried out our experiments using an Intel Core i7 6700k with 16GB RAM and NVIDIA GeForce GTX 1070.
+The environment of the experiments was Arch Linux with NVIDIA CUDA Framework ...
+and cuDNN ....
+\todo{!}
+    %Paper: Intel Core i5-7500 3.40GHz with 32GiB of RAM and NVIDIA GeForce GTX 1070 with 8GiB of memory.
+The environment of the experiments was GNU/Linux Mint 18.1, with NVIDIA CUDA Framework 9.0 and cuDNN 7.0
+
+    \subsection{Data Set: Emotion Detection}
         Unfortunately, we could not get access to the data sets used in~\cite{copycat} to compare our results with the results in the paper.
@@
 
-        In the Microsoft Azure Emotion API there is a free pricing option which allows us to submit up to 20 images per minute as well as a premium plan with up to 10 calls per second.
+        In the Microsoft Azure Emotion API there is a free pricing option which allows us to submit up to 20 images per minute as well as a standard plan with up to 10 calls per second.
 As Microsoft has a promotion for students, which gives 100€ free credit, we chose the premium plan.
@@
 Therefore, we added to the 8 emotions a further class called 'no\textunderscore face'.
+Figure~\ref{subfig:emotions_original-labels} shows the proportion of the different classes in our data set.
+In Figure~\ref{subfig:emotions_azure-labels} the distribution after classification by Azure.
+As one can see Azure could not detect about $13\%$ of the human faces.
+
+       \begin{figure}[h!]
+            \centering
+            \begin{subfigure}[c]{0.45\textwidth}
+                \centering
+                \includegraphics[width=0.95\textwidth]{exercise_3/paper/images/emotions_original-labels.png}
+                \caption{Class Distribution}
+                \label{subfig:emotions_original-labels}
+            \end{subfigure}
+            \begin{subfigure}[c]{0.45\textwidth}
+                \centering
+                \includegraphics[width=0.95\textwidth]{exercise_3/paper/images/emotions_azure-labels.png}
+                \caption{Classification of Azure}
+                \label{subfig:emotions_azure-labels}
+            \end{subfigure}
+            \caption{Performance of Copycat Attack on first data set}
+            \label{fig:emotions_distribution-labels}
+        \end{figure}
 
@@
 
-    \subsection{Evaluation 1}
+    \subsection{Evaluation of the extracted Emotion Detection model}
         Since we had labeled data, we were able to compute the accuracy of the Microsoft Azure Emotion API. On the whole data set we obtained an accuracy of $0.76$.
@@
 As we had labeled data, we had to delete the labels before querying the Azure API as a black-box.
-From now on we will refer to the training set as attack set, since this set will be used to attack the target network.
+From now on we will refer to the split for training the extracted model as attack set, since this set will be used to attack the target network.
 
@@
         \end{figure}
-        The training of the biggest extracted model took only roughly one hour, including the time needed to question the Azure API on the labeling of our data set.
-This was in part to the offer allowing students to get $100$\$ of credit for free and therefore letting us to label $10$ images per second.
-Had we used the free tier we would have needed roughly $16$ hours of time which is still a reasonable timeframe.
 
-    \subsection{Second Data Set}
-        In the following problem, we want to predict if a certain image contains a cat, a dog or none of them.
+        We took the offer for students and got $100$\$ of credit for free, which we used for the standard option. Therefore, we could label up to $10$ images per second.
+
+        Extracting a model using the whole data set took roughly one hour.
+About a third of this time was needed for training the model.
+The remaining time was for querying our target network for the labeling of our data set.
+
+        Using the free tier in Azure we would have needed about $16$ hours of time which is compared to the standard tier much longer, but still a reasonable timeframe.
+
+    \subsection{Data Set: Cats vs. Dogs}
+        In the following we have a binary classification problem, where we want to predict if a certain image contains a cat or a dog.
 
@@
 
-        \subsubsection{Cat data set}
-            %https://www.kaggle.com/crawford/cat-dataset 9000 Bilder 
-            This data set taken from \hyperlink{https://archive.org/details/CAT_DATASET}{archive.org} contains roughly $10\,000$ images of cats in various positions.
-Additionally pointers to the eyes, ears and nose of the cats were given, however we did not use them in any capacity.
+        \subsubsection{Dogs vs. Cats}
+            Instead of using an already existing API, in this experiment we chose to train our own CNN to steal to make matters more interesting.
+We obtained the training set for building our target model from the Kaggle competition 'Dogs vs.
+Cats'~\cite{dogs-cats}.
+It contains $25\,000$ images of cats and dogs including its labels.
 
-        \subsubsection{Stanford dogs data set }
-            The data set was built using images from ImageNet, by \hyperlink{http://vision.stanford.edu/aditya86/ImageNetDogs/}{Stanford university} , in order to help categorize images.
-It contains $20\,580$ pictures of dogs.
-It theoretically contains classifications for different breeds of dogs, but once again we did not use this.
+            Additionally, this Kaggle competition provided another data set with $12\,500$ pictures of cats and dogs, but without labels, as the goal of the competition was to predict these labels.
+Since the attack set does not need any labeled data, we decided to use this set as part of the attack set.
+
+        \subsubsection{Cats}
+            This data set is also from Kaggle~\cite{cats}. It contains roughly $10\,000$ images solely of cats in various positions. 
+            In an additional file more information, like pointers to the eyes, ears and nose of the cats in the pictures, can be found. However we did not use them in any capacity.
+
+            We used this data set as part of the attack and test set.
+
+        \subsubsection{Stanford dogs data set}
+            The Stanford dogs data set ~\cite{dogs} was built using images from ImageNet in order to help categorize images.
+It contains $20\,580$ pictures purely of dogs.
+Additionally, it contains also classification for different breeds of dogs, but once again we did not use this information in out attack.
+
+            In our experiment this data set was used in the attack and test set.
 
         \subsubsection{Common objects in context data set}
-            Since our model for this exercise was homemade, we could use copy-cat to it's full power and include non-domain data in our training set for our copy-cat model.
-For this we chose a dataset from \hyperlink{https://cocodataset.org/\#download}{Common objects in context} containing $118\,000$ images of trains.
+            Since we construct the target network in this experiment by ourselves, we can use the copycat attack to it's full power and include non-problem domain data in our attack set. 
+            For this we chose the COCO (Common Objects in Context) data set~\cite{coco}, which is known for object detection, segmentation and captioning.
+With a size of about $118\,000$ images it is a large data set.
 
-     \subsection{Dogs vs. Cats}
-            For the second attempt we chose to train our own CNN to steal to make matters more interesting.
-We trained our model using the following competition data set from \hyperlink{https://www.kaggle.com/c/dogs-vs-cats/data}{Kaggle}.
-We trained it using the training set containing $25\,000$ images of cats and dogs.
+            These images will only be used in the attack set, since the classification problem is to decide if a picture shows a dog or a cat, but not to decide if it is something else.
+Moreover, since the images in this data set do not contain to our problem domain and compared to the number of our problem-domain data is much bigger, we decided not to use the whole data set.
 
-            We tested the accuracy of the set by mixing the cat data set and the Stanford dog data set and picking $7\,644$ random images out of it. The resulting accuracy was $0\,821$.
-    \subsection{Evaluation 2}
+    \subsection{Evaluation of the extracted Cats vs. Dogs model}
+        We tested the accuracy of the set by mixing the cat data set and the Stanford dog data set and picking $7\,644$ random images out of it. The resulting accuracy was $0,821$.
+
+        -------------------------------------------------------------------
+
         We extracted the model in two different ways.
@@
                 \centering
-                \includegraphics[width=1\textwidth]{exercise_3/paper/images/accuracy_copy_cat.png}
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat_domain.png}
                 \caption{Accuracy using only problem domain}
-                \label{fig:Accuracy_Azure}
+                \label{fig:Accuracy_Cat_domain}
             \end{subfigure}
@@
                 \centering
-                \includegraphics[width=1\textwidth]{exercise_3/paper/images/equality_copy_cat_.png}
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat.png}
                 \caption{Accuracy using mixed instances }
-                \label{fig:Equality_Azure}
+                \label{fig:Accuracy_cat_mix}
             \end{subfigure}
-            \caption{Performance of Copycat Attack on first data set}
-            \label{fig:performance-azure}
+            \caption{Accuracy of Copycat Attack on second data set}
+            \label{fig:accuracy_cat}
+        \end{figure}
+        It is visible, that in case of the attack set being of similar size the attack set consisting only of instances, that are part of the problem domain performed better.
+
+        Looking at how much of the data our extracted model labeled the same as the original model, showed the same:
+         \begin{figure}[h!]
+            \centering
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat_domain.png}
+                \caption{Equality using only problem domain}
+                \label{fig:Equality_cat_domain}
+            \end{subfigure}
+            \begin{subfigure}[c]{0.49\textwidth}
+                \centering
+                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat.png}
+                \caption{Equality using mixed instances}
+                \label{fig:Equality_cat_mix}
+            \end{subfigure}
+            \caption{Equality of Copycat Attack on second data set}
+            \label{fig:equality_cat}
+        \end{figure}
+    Once again using only problem domain data performed better, when looking at attack sets of similar size.
+
+    The time needed to train the models grew roughly linearly with the size of the attack sets.
+The largest attack set of size $94\,572$ trained the extracted model in roughly $24$ minutes.
+Below is the time needed to construct the extracted model compared to the size of the attack set.
+        \begin{figure}[h!]
+            \centering      \includegraphics[scale=0.2]{exercise_3/paper/images/Time_copy_cat.png}
+            \caption{Time needed to extract a model}
+            \label{fig:time_cat}
         \end{figure}
 
-\section{last classifier}
+\section{Decision Tree Path-Finding Attack}
+    As the name suggests, this model extraction method targets decision tree models.
+Such a model divides the input space into several discrete partitions.
+The idea behind the decision tree path-finding attack is to vary the values of each feature bit by bit to find the value at which the tree splits.
+
+    We carried out our experiments using GCP e2-highmem-16 offered by the Google Cloud Platform running on Ubuntu 20.04.
+
+    \subsection{Data Set}
+        ...
+
+    \subsection{Evaluation}
+        ...
+
 \section{Conclusions}
+    The copy-cat method in general performed extremely well, getting an equality of roughly $0,7$ even on the rather complex Microsoft Azure emotional API in less than one hour and using a rather small attack set.
+While using only instances that are part of the problem domain worked better on similar attack set sizes, finding instances that are not part of the problem domain is an easier task in general and still works pretty well.
+Taking this into consideration, in case that the number of queries on can make to the blackbox is severely limited or run time is an important factor, one should rely mainly on problem domain instances.
+Should this not be the case non-problem domain instances allow for a quick assembly of a large data set that can extract a model reasonably well.
 

### 2021-02-21 exercise_3/paper/paper_ex3.tex

@@
 
-    We carried out our experiments using an Intel Core i7 6700k with 16GB RAM and NVIDIA GeForce GTX 1070.
-The environment of the experiments was Arch Linux with NVIDIA CUDA Framework ...
-and cuDNN ....
-\todo{!}
-    %Paper: Intel Core i5-7500 3.40GHz with 32GiB of RAM and NVIDIA GeForce GTX 1070 with 8GiB of memory.
-The environment of the experiments was GNU/Linux Mint 18.1, with NVIDIA CUDA Framework 9.0 and cuDNN 7.0
+    We carried out our experiments using an Intel Core i7 6700k with 16GB RAM and NVIDIA GeForce GTX 1070. The environment of the experiments was Arch Linux with NVIDIA CUDA 10.2 and cuDNN 7.6.5.
 
@@
 
-        \subsubsection{KDEF and AKDEF}
+        \subsubsection{KDEF and AKDEF} \label{subsec:dataset_KDEF-AKDEF}
             The Karolinska directed emotional faces data set~\cite{kdef} (short KDEF) contains 4\,900 images of human facial expressions.
@@
 
-        \subsubsection{Emotion Detection from Facial Expressions}
+        \subsubsection{Emotion Detection from Facial Expressions} \label{subsec:dataset_kaggle-emotions}
             This data set was taken from the Kaggle competition 'Emotion Detection From Facial Expressions'~\cite{kaggle-emotion}. 
@@
 
-        For testing the efficiency of our extracted model, we initially did a $75\%/25\%$ training/test split on our data set consisting of KDEF, AKDEF and the one from Kaggle.
+        For testing the efficiency of our extracted model, we initially did a $75\%/25\%$ training/test split on our data set consisting of KDEF, AKDEF (see Subsection~\ref{subsec:dataset_KDEF-AKDEF}) and the one from Kaggle (see Subsection~\ref{subsec:dataset_kaggle-emotions}).
 As we had labeled data, we had to delete the labels before querying the Azure API as a black-box.
@@
 We trained the model on progressively larger subsets of the training set, which were included in each other.
-Starting with a random sample $s_0$ of $2\,000$ images, the next training set $s_n$ consisted of $s_{n-1}$ and additional $1\,000$ images.
+Starting with a random sample $s_0$ of $2\,000$ images, the next training set $s_n$ consisted of $s_{n-1}$ and additional $1\,000$ randomly selected images, which are not already contained in $s_{n-1}$.
 
@@
 
-        We took the offer for students and got $100$\$ of credit for free, which we used for the standard option. Therefore, we could label up to $10$ images per second.
+        We took the offer for students and got $100$\$ of credit for free, which we used for the standard option.
+Therefore, we could label up to $10$ images per second but had to pay $0.01$\$ per $1\,000$ calls.
 
@@
 
-    \subsection{Data Set: Cats vs. Dogs}
+    \subsection{Data Sets: Cats vs. Dogs}
         In the following we have a binary classification problem, where we want to predict if a certain image contains a cat or a dog.
@@
 
-        \subsubsection{Dogs vs. Cats}
+        \subsubsection{Dogs vs. Cats}\label{subsec:dataset_cats-dogs}
             Instead of using an already existing API, in this experiment we chose to train our own CNN to steal to make matters more interesting.
@@
 Cats'~\cite{dogs-cats}.
-It contains $25\,000$ images of cats and dogs including its labels.
+It contains in total $25\,000$ images including its labels, where half of the images picture cats and the other half dogs.
 
@@
 
-        \subsubsection{Cats}
+        \subsubsection{Cats} \label{subsec:dataset_cats}
             This data set is also from Kaggle~\cite{cats}. It contains roughly $10\,000$ images solely of cats in various positions. 
@@
 
-        \subsubsection{Stanford dogs data set}
+        \subsubsection{Stanford dogs data set} \label{subsec:dataset_dogs}
             The Stanford dogs data set ~\cite{dogs} was built using images from ImageNet in order to help categorize images.
@@
 
-        \subsubsection{Common objects in context data set}
+        \subsubsection{Common objects in context data set}\label{subsec:dataset-coco}
             Since we construct the target network in this experiment by ourselves, we can use the copycat attack to it's full power and include non-problem domain data in our attack set. 
-            For this we chose the COCO (Common Objects in Context) data set~\cite{coco}, which is known for object detection, segmentation and captioning.
+            For this we chose the Microsoft COCO (Common Objects in Context) data set~\cite{coco}, which is known for object detection, segmentation and captioning.
 With a size of about $118\,000$ images it is a large data set.
@@
 
-    \subsection{Evaluation of the extracted Cats vs. Dogs model}
-        We tested the accuracy of the set by mixing the cat data set and the Stanford dog data set and picking $7\,644$ random images out of it. The resulting accuracy was $0,821$.
+    \subsection{Target Network}
+        The targeted CNN was trained using the Dogs vs.
+Cats data set from Kaggle (see Subsection~\ref{subsec:dataset_cats-dogs}).
+We build a CNN consisting of 3 Convolutional layer blocks and a fully connected layer.
+In each Convolutional layer block we are applying
+        \begin{itemize}
+            \item 2D convolutions two times with a kernel size of 3 and padding value of 1,
+            \item Batch Normalisation,
+            \item ReLU as activation function,
+            \item Max Pooling with a kernel size of 2 and a stride of 2. 
+        \end{itemize}
+        In the fully connected layer we are applying the following methods several times:
+        \begin{itemize}
+            \item Dropout with $p=0.1$ (probability of an element to be zeroed),
+            \item linear transformation,
+            \item ReLU.
+        \end{itemize}
 
-        -------------------------------------------------------------------
+       We trained the target model for 10 epochs and using Stochastic Gradient Descent with a Step Down policy for the learning rate and CrossEntropyLoss as criterion.
+In the augmentation step we resized the images.
+
+       This model achieved an accuracy of $0,821$ on the test data set (see Subsection~\ref{subsec:evaluation-cats-dogs} for more detailed description and analysis).
+
+    \subsection{Evaluation of the extracted Cats vs. Dogs model}~\label{subsec:evaluation-cats-dogs}
+        As our test set we made a $25\%$ split on the Cats (see Subsection~\ref{subsec:dataset_cats}) and the Dogs (see Subsection~\ref{subsec:dataset_dogs}) data set.
 
         We extracted the model in two different ways.
-In one instance we used only images that are part of the domain, therefore pictures of cats and dogs, in the attack set.
-In the other instance we used a mixture of non-domain images and domain images in a $2$ to $5$ ratio, to let the original model confess its information.
+First, we used only images that are part of the domain, therefore pictures of cats and dogs, in the attack set.
+For this we combined the remaining $75\%$ of the Cats and Dogs images with the unlabeled data of the Cats vs.
+Dogs data set (see Subsection~\ref{subsec:dataset_cats-dogs}).
+        For evaluation we proceeded similarly to the Emotion Detection problem.
+We started with a random subset with $3\,000$ images as our attack set and extracted a model.
+Then we iteratively increased the size of the attack size by $3\,000$ images and in each step extracted another model until we used all of the available images for the model-stealing attack.
 
-        We start by looking at the accuracy of the extracted model in both cases:
+        Moreover, we also experimented also with a mixture of non-problem domain (short NPD) images and problem domain (short PD) images in the attack set.
+For this we added half of the COCO data set (see Subsection~\ref{subsec:dataset-coco}) to our attack set.
+The ratio between the PD and NPD instances in the total set was $2:5$.
+        The testing phase including NPD images was similar to the PD case.
+As we had much more images in this case, we started with an initial attack set of $5\,000$ images and increased its size in each step by $10\,000$ pictures.
+
+        Our experiments had the following results.
+Figure~\ref{fig:accuracy_cat} shows the accuracy for each of the two approaches with increasing number of instances in the attack set.
+As we can see in the case, where only PD data is used to attack, there is a slight increase for larger attack sets from $0.632$ to $0.768$, but the difference is not very much.
+
+        Considering the second case in Figure~\ref{fig:accuracy_cat_PD+NPD}, where also NPD data is included, we can see that this looks similar to the other approach.
+The accuracy increases from $0.673$ to $0.791$.
+
         \begin{figure}[h!]
@@
             \begin{subfigure}[c]{0.49\textwidth}
-                \centering
-                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat_domain.png}
-                \caption{Accuracy using only problem domain}
-                \label{fig:Accuracy_Cat_domain}
+                \centering                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat_domain.png}
+                \caption{Accuracy using only PD data}
+                \label{fig:accuracy_cat_PD}
             \end{subfigure}
             \begin{subfigure}[c]{0.49\textwidth}
-                \centering
-                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat.png}
-                \caption{Accuracy using mixed instances }
-                \label{fig:Accuracy_cat_mix}
+                \centering                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat.png}
+                \caption{Accuracy including also NPD data}
+                \label{fig:accuracy_cat_PD+NPD}
             \end{subfigure}
@@
         \end{figure}
-        It is visible, that in case of the attack set being of similar size the attack set consisting only of instances, that are part of the problem domain performed better.
 
-        Looking at how much of the data our extracted model labeled the same as the original model, showed the same:
+        Furthermore, we will consider the equality of our extracted model. In Figure~\ref{fig:equality_cat} we can see that graph for both approaches looks very similar.
+
          \begin{figure}[h!]
@@
             \begin{subfigure}[c]{0.49\textwidth}
-                \centering
-                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat_domain.png}
-                \caption{Equality using only problem domain}
-                \label{fig:Equality_cat_domain}
+                \centering                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat_domain.png}
+                \caption{Equality using only PD data}
+                \label{fig:Equality_cat_PD}
             \end{subfigure}
             \begin{subfigure}[c]{0.49\textwidth}
-                \centering
-                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat.png}
-                \caption{Equality using mixed instances}
-                \label{fig:Equality_cat_mix}
+                \centering                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat.png}
+                \caption{Equality including also NPD data}
+                \label{fig:equality_cat_PD+NPD}
             \end{subfigure}
@@
         \end{figure}
+
+        It is visible, that in case of the attack set being of similar size the attack set consisting only of instances, that are part of the problem domain performed better.
+
         Once again using only problem domain data performed better, when looking at attack sets of similar size.
+
+                %the number of instances in the attack set has more visible influence on the accuracy of the extracted model. The accuracy increases from $0.673$ to $0.791$.
 
@@
         \begin{figure}[h!]
-            \centering      \includegraphics[scale=0.2]{exercise_3/paper/images/Time_copy_cat.png}
+            \centering      \includegraphics[width=0.6\textwidth]{exercise_3/paper/images/Time_copy_cat.png}
             \caption{Time needed to extract a model}
@@
 
+        ------------------------------------------------------------------
+
+        We tested the accuracy of the set by mixing the cat data set and the Stanford dog data set and picking $7\,644$ random images out of it. The resulting accuracy was $0,821$.
+
 \section{Decision Tree Path-Finding Attack}
-    As the name suggests, this model extraction method targets decision tree models.
+    As the name suggests this model stealing attack targets decision tree models.
 Such a model divides the input space into several discrete partitions.
 The idea behind the decision tree path-finding attack is to vary the values of each feature bit by bit to find the value at which the tree splits.
+Algorithm~\ref{alg:DT-attack} you can find a rough sketch of this attack.
+In this pseudocode let $Q$ be the set of unprocessed queries and $P$ the set of explored leaves with their classification.
+
+    \begin{algorithm}
+        \caption{Path-finding attack for decision trees}
+	    \begin{algorithmic}[1]
+%		    \State Let $Q$ be the set of unprocessed queries;
+%		    \State Let $P$ be the set of explored leaves with their classification;
+		    \State Add a random first query to $x_{init}$ to $Q$;
+		    \State While $Q\neq\emptyset$ process $x\in Q$;
+		    \State Do binary search over the continous features and check whether a new leaf can be discovered;
+		    \State in this way explore the continuous features and variate the discrete features to find all leaves;
+	    \end{algorithmic}
+	    \label{alg:DT-attack}
+    \end{algorithm}
+    A weakness of this approach is that if two instances that lead to different leaves that are classified as the same, only differ in a single feature, the difference may not be registered in the extracted model.
 
@@
 
-    \subsection{Data Set}
-        ...
+    \subsection{Models}
+        Since this extraction method does not use data sets to get the model to confess its knowledge, we instead look at publicly available decision tree models from bigml which we are looking to extract.
+        \subsubsection{US IRS 2008 tax data patterns}
+        https://bigml.com/user/francisco/gallery/model/50c008bb3b56351981000375
+        This decision tree was generated using data from tax returns filed in the US in 2009. The decision tree aims to predict the home state of the tax payer.
+        \subsubsection{Steak survey}
+        https://bigml.com/user/ashikiar/gallery/model/537be4c3d9949779990041e9
+        This model was based on data from a \hyperlink{https://fivethirtyeight.com/features/how-americans-like-their-steak/}{FiveThirtyEighty survey}, which asked a lot of general questions as well as how they liked their steak prepared (Rare, Medium-rare, Medium, Medium-well, Well).
+        \subsubsection{Bitcoin price} 
+        https://bigml.com/user/czuriaga/gallery/model/51ccb90a035d07603900039e
+        Was macht der TREEEE?????
+        \subsubsection{Email Importance}
+        https://bigml.com/user/louisdorard/gallery/model/52fa8aa60c0b5e6d4a0030c1
 
+        This model was built using Email data collected from the users own inbox.
+The importance was set by Gmail.
+Using a variety of features including length of the mail and whether the mail was sent by a contact, the tree classifies the importance.
+        \subsubsection{gss survey}
+        Find das model ned
+        \subsubsection{med price}
+        Find ich ned
     \subsection{Evaluation}

### 2021-02-21 exercise_3/paper/paper_ex3.tex

@@
 \setlength{\footheight}{29pt}
+
+%%%%%%%% Biblatex
+\usepackage[backend=biber,style=numeric,sortlocale=de_DE,natbib=true,url=false, doi=true,eprint=false]{biblatex}
+\addbibresource{literature.bib}
 
@@
 As one can see Azure could not detect about $13\%$ of the human faces.
+We only performed a copycat attack with a problem domain dataset for this reason, since the Azure Emotion API in the current version does not allow us to extract emotions for images without an detected face.
 
@@
         \end{figure}
-
-        %Originally, we wanted to add instances, which are not part of the problem domain to our fake data set.
-However, as Azure does not classify images in which it does not detect any face, this was not possible.
 
@@
 Overall it can be seen that the accuracy as well as the equality improve for larger training sets.
-The best value for the accuracy in our tests was $0.578$.
-which seems much better compared to the results from the paper with about $0.35$.
-We also computed the accuracy of the Azure Emotion API on the test set and obtained an accuracy of $0.764$.
+The best value for the accuracy in our tests was $0.578$ which seems much better compared to the results from the paper with about $0.35$ depending on the attack data set.
+Nevertheless, the Azure Model used in the paper (which was an older version) also had an accuracy of around $0.351$.
+We also computed the accuracy of the Azure Emotion API on the test set and obtained an accuracy of $0.764$, which is much better than the accuracy recorded in the paper.
+Therefore our performance was $0.756$ compared to the target network.
 
-        However, the extracted model using the whole training set was was able to coincide on $70\%$ on the test data.
+        The extracted model using the whole attack set was was able to coincide on $70\%$ with the azure classifications on our test set.
 
@@
         We took the offer for students and got $100$\$ of credit for free, which we used for the standard option.
-Therefore, we could label up to $10$ images per second but had to pay $0.01$\$ per $1\,000$ calls.
+Therefore, we could label up to $10$ images per second but had to pay $1$\$ per $1\,000$ calls.
 
@@
 
+        The accuracy of the target model on the same test set was $0,821$. 
+        Comparing the accuracy of the extracted models in our tests to the accuracy of the target CNN we can see that this measure is very close to the original one.
+
         \begin{figure}[h!]
@@
 
-        Furthermore, we will consider the equality of our extracted model. In Figure~\ref{fig:equality_cat} we can see that graph for both approaches looks very similar.
+        Furthermore, we will consider the equality of our extracted model.
+In Figure~\ref{fig:equality_cat} we can see that the two graphs for both approaches look very similar.
+For a larger attack set the equality can be improved up to $0.864$.
+This means, compared to the previous Emotion Detection problem, we were able to copy the model in this setting better in these tests and on the given data.
 
@@
 
-        It is visible, that in case of the attack set being of similar size the attack set consisting only of instances, that are part of the problem domain performed better.
+        In addition to that, we will also look at how much time it takes to train the extracted model for an attack set of certain size.
+As it can be seen in Figure~\ref{fig:time_cat} the time for training the models grew roughly linear with the size of the attack set in our tests.
+The largest attack set containing $94\,572$ images needed about $24$ minutes to perform the attack, i.e.
+to build the extracted model.
 
-        Once again using only problem domain data performed better, when looking at attack sets of similar size.
-
-                %the number of instances in the attack set has more visible influence on the accuracy of the extracted model. The accuracy increases from $0.673$ to $0.791$.
-
-    The time needed to train the models grew roughly linearly with the size of the attack sets.
-The largest attack set of size $94\,572$ trained the extracted model in roughly $24$ minutes.
-Below is the time needed to construct the extracted model compared to the size of the attack set.
         \begin{figure}[h!]
-            \centering      \includegraphics[width=0.6\textwidth]{exercise_3/paper/images/Time_copy_cat.png}
+            \centering      \includegraphics[width=0.65\textwidth]{exercise_3/paper/images/Time_copy_cat.png}
             \caption{Time needed to extract a model}
@@
 
-        ------------------------------------------------------------------
-
-        We tested the accuracy of the set by mixing the cat data set and the Stanford dog data set and picking $7\,644$ random images out of it. The resulting accuracy was $0,821$.
+        Summarizing it can be said that for a fixed number of PD data, adding NPD images improves the accuracy and equality of the extracted model.
+But since more queries to the target network are required when adding NPD data, the time needed for building the model increases.
+Hence, there is a trade-off between the performance of the model and the costs.
 
@@
 Such a model divides the input space into several discrete partitions.
-The idea behind the decision tree path-finding attack is to vary the values of each feature bit by bit to find the value at which the tree splits.
-Algorithm~\ref{alg:DT-attack} you can find a rough sketch of this attack.
-In this pseudocode let $Q$ be the set of unprocessed queries and $P$ the set of explored leaves with their classification.
+The idea behind the decision tree path-finding attack is to vary the values of each feature bit by bit and then to query the black-box to find the values at which the tree splits.
+In Algorithm~\ref{alg:DT-attack} you can find a rough sketch of this attack.
+In this pseudocode let $Q$ be the set of unprocessed queries and $P$ the set of explored leaves with their classification value.
 
@@
     \end{algorithm}
-    A weakness of this approach is that if two instances that lead to different leaves that are classified as the same, only differ in a single feature, the difference may not be registered in the extracted model.
+
+    A weakness of this approach is that for two instances which e.g.
+only differ in a single feature, the target decision tree leads to different leaves which are classified as the same, the difference may not be registered in the extracted model.
 
@@
     \subsection{Models}
-        Since this extraction method does not use data sets to get the model to confess its knowledge, we instead look at publicly available decision tree models from bigml which we are looking to extract.
+        Since this model stealing attack does not use attack sets to get the model (like the previous one) to confess its knowledge, we looked at publicly available decision tree models from BigML instead of data sets.
+
+        Moreover, we decided to consider the models from the paper to find out if this model stealing attack implemented exactly as in the paper but performed in a different setting yields to exactly the same extracted model or if it leads to any differences.
+
         \subsubsection{US IRS 2008 tax data patterns}
-        https://bigml.com/user/francisco/gallery/model/50c008bb3b56351981000375
-        This decision tree was generated using data from tax returns filed in the US in 2009. The decision tree aims to predict the home state of the tax payer.
+            The decision tree for US IRS 2008 tax data patterns~\cite{tax} was generated using data from tax returns filed in the US in 2008.
+The decision tree aims to predict the home state of the tax payer depending, e.g.
+on the unemployment compensation, real estate taxes or the tax due at time of filing.
+
         \subsubsection{Steak survey}
-        https://bigml.com/user/ashikiar/gallery/model/537be4c3d9949779990041e9
+
             This model was based on data from a \hyperlink{https://fivethirtyeight.com/features/how-americans-like-their-steak/}{FiveThirtyEighty survey}, which asked a lot of general questions as well as how they liked their steak prepared (Rare, Medium-rare, Medium, Medium-well, Well).
+
         \subsubsection{Bitcoin price} 
@@
             Was macht der TREEEE?????
+
         \subsubsection{Email Importance}
@@
 Using a variety of features including length of the mail and whether the mail was sent by a contact, the tree classifies the importance.
+
         \subsubsection{gss survey}
             Find das model ned
+
         \subsubsection{med price}
             Find ich ned
+
     \subsection{Evaluation}
@@
 
-\bibliographystyle{abbrv}
-\bibliography{literature}
+\printbibliography
 
